---
title: "Clean raw data updated to 2025-09-08"
output: html_document
---
#load packages
```{r}
rm(list = ls())
suppressPackageStartupMessages({
  require(pacman)
  pacman::p_load(openxlsx,
                 data.table,
                 magrittr,
                 dplyr,
                 rlang,
                 countrycode,
                 lubridate,
                 purrr,
                 stringr)
})
```
# Define working directory
```{r}
wd <- "./"
setwd(wd)
```
# Import raw data
```{r}
path <- "data/raw data/"
fileNames <- dir(path)
filePath <- sapply(fileNames, 
                   function(x){paste(path, x, sep = '/')})
# The sequence from data[[1]] to data[[10]] is as follows: 
# F01, F02, F03, F04, F07a, F07b, F07c, F07d, F07e, F07m.
data <- lapply(filePath, function(x){fread(x, fill = TRUE)})
# Anti group
anti <- read.xlsx("data/anti group/anti_group_used.xlsx")
org_anti_class <- read.xlsx("data/anti group/organism_group.xlsx") 

###
# Loop through the first 10 elements of data, convert to data frames and convert IDate columns to Date
for (i in 1:10) {
  # Convert the current element to a data frame
  data[[i]] <- as.data.frame(data[[i]])
  
  # Convert all IDate columns to Date in the current data frame
  data[[i]] <- data[[i]] %>%
    mutate(across(where(~ inherits(.x, "IDate")), ~ as.Date(.x)))
}
```
# Revise redcap_repeat_instance 2 ~ 1 due to delete
```{r}
revise_dele <- which((data[[2]]$recordid %in% c("BN-001-A0-0002", "MY-004-A0-0095", "PK-001-A0-0033")) & (data[[2]]$redcap_event_name == "bsi_episode_arm_1"))

data[[2]]$redcap_repeat_instance[revise_dele] <- 1

```
# Divide three groups (infection types)
```{r}
#####
# VAP
# Hospital-acquired BSI 
# If not transfer: inf_onset-hpd_adm_date>2days; 
# If transfer: inf_onset-hpd_hosp_date>2days 
# Healthcare-associated BSI 
# If not transfer:inf_onset-hpd_adm_date<=2days;
# If transfer:inf_onset-hpd_hosp_date<=2days
#####
## VAP
vap_onset_data <- data[[6]]
vap_onset_data$infection_types <- "VAP"
## BSI
# hpd_hosp_date
baseline_hosp <- data[[1]] %>% 
  select("recordid", "hpd_hosp_date", "hpd_adm_date")
# Combine hpd_hosp_date, hpd_adm_date, and inf_onset
bsi_onset_data <- left_join(data[[5]], baseline_hosp, by = "recordid")
#
bsi_onset <- as.Date(bsi_onset_data$inf_onset, format = "%Y-%m-%d")
bsi_adm <- as.Date(bsi_onset_data$hpd_adm_date, format = "%Y-%m-%d")
bsi_hosp <- as.Date(bsi_onset_data$hpd_hosp_date, format = "%Y-%m-%d")
# The difference between dates 
adm_diff <- difftime(bsi_onset, bsi_adm, units = "days")
hosp_diff <- difftime(bsi_onset, bsi_hosp, units = "days")
# Hospital-acquired BSI
bsi_onset_data$infection_types[(adm_diff > 2) | (hosp_diff > 2)] <- "Hospital-acquired BSI"
# Healthcare-associated BSI
bsi_onset_data$infection_types[(adm_diff <= 2) | (hosp_diff <= 2)] <- "Healthcare-associated BSI"
###
# Index onset date of vap or bsi
vap_index <- vap_onset_data[(which(vap_onset_data$redcap_repeat_instance == 1)),]
bsi_index <- bsi_onset_data[(which(bsi_onset_data$redcap_repeat_instance == 1)),]
# Earlier infection onset date
df_vap_index <- vap_index %>% 
  select("recordid", "inf_onset2", "infection_types")

df_bsi_index <- bsi_index %>% 
  select("recordid", "inf_onset", "infection_types")

# 
combined_df_ori <- bind_rows(df_vap_index, df_bsi_index) %>%
  mutate(combined_onset = coalesce(inf_onset2, inf_onset)) %>% 
  select(-inf_onset2, -inf_onset) %>% 
  rename(inf_onset = combined_onset) %>%
  filter(!is.na(infection_types))

# -----------------------------
# Check the duplicate
# Find recordids with duplicate combined_onset
duplicate_recordids <- combined_df_ori %>%
  group_by(recordid, inf_onset) %>%
  filter(n() > 1) %>%
  distinct(recordid) %>%
  pull(recordid)

# Extract rows from the original dataframe where these recordid occur
duplicate_rows <- combined_df_ori %>%
  filter(recordid %in% duplicate_recordids) %>%
  arrange(recordid, inf_onset)

```
# AST
```{r}
# AST result
ast_results <- data[[10]] %>% 
  select(starts_with("susceptibility_")) %>%
  mutate(across(everything(), as.numeric))

# Replace NA
ast_results[is.na(ast_results)] <- 5

# Add other variables
ast_add <- data[[10]] %>% 
  select("recordid", "org", "org_oth",
         "f07m_bsic", "f07m_vapc", 
         "ast_date", "spec_date", 
         "f07m_hpd_adm_date_1", "f07m_hpd_adm_date_2",
         "redcap_repeat_instance")

# Define the organism names
org_names <- c("E. coli", "K. pneumoniae", "Acinetobacter spp.", "Pseudomonas spp.",
               "Serratia", "Proteus", "Morganella", "Enterobacter",
               "Stenotrophomonas spp.", "S. aureus", "Enterococcus spp.", 
               "S. pneumoniae", "Candida spp.", "Others")

# Add the organism names to the ast_add dataframe
ast_add$org_names <- factor(ast_add$org, levels = 1:14, labels = org_names)

# Add other names
ast_add$org_names_all <- ifelse(ast_add$org_names == "Others", ast_add$org_oth, as.character(ast_add$org_names))

# 
name_mapping <- c(
"A.baumannii" = "Acinetobacter spp.",
"acinetobacter baummanii" = "Acinetobacter spp.",
"Acinetobacter nosocomialis" = "Acinetobacter spp.",
"Acinetobactor" = "Acinetobacter spp.",
"ABIOTROPHIA DEFECTIVA" = "Abiotrophia",                                      
"Achromobacter" = "Achromobacter",                                                
"ACHROMOBACTER DENTRIFICANS" = "Achromobacter",
"achromobacter denitrificans" = "Achromobacter",
"Achromobacter species" = "Achromobacter",                                        
"Achromobacter spp" = "Achromobacter",                                   
"Achromobacter xylosoxidans" = "Achromobacter",                         
"Achromobacter xylosoxidans " = "Achromobacter",                          
"Achromobacter xylosoxodans" = "Achromobacter",               
"Achromobacter xyloxosidans" = "Achromobacter",
"Achromobacter mucicolens" = "Achromobacter",
"Achromobacter xylosoxidans ss dentrificans" = "Achromobacter",
"acinetobacter baumannii" = "Acinetobacter spp.",                     
"acinetobacter lwoffii" = "Acinetobacter spp.",                        
"acinetobactor baumani complex" = "Acinetobacter spp.", 
"Acinetobacter Nosocomial " = "Acinetobacter spp.", 
"ACINOBACTER IWOFPII" = "Acinetobacter spp.",
"Acinetobacter junii" = "Acinetobacter spp.",
"acromonas hydrophilia&Klebsiella oxytoca" = "Aeromonas",                         
"Actinomyces odontolyticus" = "Actinomyces",                                      
"Aerobic Actinomycetes" = "Actinomyces",
"aeromanas" = "Aeromonas",
"Aeromonas caviae" = "Aeromonas",                                                 
"Aeromonas caviae complex" = "Aeromonas",                                         
"aeromonas hydrophila" = "Aeromonas",                                             
"Aeromonas hydrophila" = "Aeromonas",                                              
"Aeromonas hydrophila complex" = "Aeromonas",                                     
"Aeromonas hydrophila/caviae 1" = "Aeromonas",                                    
"Aeromonas hydrophila/caviae 2" = "Aeromonas",
"Aeromonas hydrophilacaviae" = "Aeromonas",
"Aeromonas hydrophili complex" = "Aeromonas",
"aeromanas hydrophila complex" = "Aeromonas",
"AEROMONAS HYDROPHILIA" = "Aeromonas",                                            
"Aeromonas punctata " = "Aeromonas",                                              
"Aeromonas punctata (caviae)" = "Aeromonas",                                      
"Aeromonas sp." = "Aeromonas",                                                    
"Aeromonas species" = "Aeromonas",                                                
"AEROMONAS SPECIES" = "Aeromonas", 
"Aeromonas sobria" = "Aeromonas", 
"Aeromonas veronii" = "Aeromonas",                                                
"AEROMONAS VERONII" = "Aeromonas",
"Aeromonas veronii biovar. sobria" = "Aeromonas",                                 
"Aeromonas veronii bv sobria" = "Aeromonas",
"Aeromonas veronii complex" = "Aeromonas",
"A.hydrophilalcaviae" = "Aeromonas",
"Aeromonas hydrophia/caviae" = "Aeromonas",
"AEROCOCCUS VIRIDANS" = "Aerococcus",
"AEROCOCCUS URINAE" = "Aerococcus",

" Agrobacterium radiobacter" = "Agrobacterium", 
"Agrobacterium radiobacter" = "Agrobacterium", 
"Anaerococcus prevottii" = "Anaerococcus",                                         
"ANTROBACTER FECUNDIL" = NA,                                                      
"Arthrobacter spp" = "Arthrobacter",                                              
"Aspergillus spp" = "Aspergillus",
"Aspergillus fumigatus " = "Aspergillus",
"Aspergillus fumigatus complex" = "Aspergillus",

"B. cepaciae" = "Burkholderia",                                                         
"Bacillus cereus" = "Bacillus",                                                   
"Bacillus cereus group" = "Bacillus",                                             
"bacillus species" = "Bacillus",                                                  
"Bacillus species" = "Bacillus",                                                  
"Bacillus spp." = "Bacillus",                                                     
"BACILLUS SUBTILIS" = "Bacillus",
"BACILLUS CEREUS (X2 SITES)" = "Bacillus",
"Bacillus cereus/thuringiensis/mycoides" = "Bacillus",

"Bacteroides fragilis group" = "Bacteroides",
"Bacteroides fragilis" = "Bacteroides",
"BACTEROIDES FRAGILIS" = "Bacteroides",
"BACTEROIDES SALYERSIAE" = "Bacteroides",                                          
"Bacteroides thetaiotaomicron" = "Bacteroides",
"Bacteroides caccae" = "Bacteroides",
"Bipolaris cactivora" = "Bipolaris",                                        
"Blinkholderia gladioli" = NA,

"Bulcoldoria Cepace complex" = "Burkholderia",
"Bukholderia cenocepacia" = "Burkholderia",                                        
"Bukholderia cepacia" = "Burkholderia",                                            
"Bukholderia contaminans" = "Burkholderia",                                        
"Bulkhoderia cepacia" = "Burkholderia",                           
"Bulkhoderia cepacia complex" = "Burkholderia",
"Burkholderia Cepacciae Complex " = "Burkholderia",

"Bulkhoderia gladioli" = NA,                                                       
"Burkhoderia cepacia complex" = "Burkholderia",                                    
"Burkholdeeria cepacia" = "Burkholderia",                                          
"BURKHOLDENA CEPACIA" = "Burkholderia",                                            
"Burkholderia" = "Burkholderia",                                                   
"Burkholderia cenocepacia" = "Burkholderia",                                       
"burkholderia cepacia" = "Burkholderia",                                           
"Burkholderia cepacia" = "Burkholderia",                                           
"Burkholderia Cepacia" = "Burkholderia",                                           
"Burkholderia cepacia " = "Burkholderia",                                          
"Burkholderia cepacia complex" = "Burkholderia",                                   
"BURKHOLDERIA CEPACIA COMPLEX" = "Burkholderia",                                   
"Burkholderia cepacia group" = "Burkholderia",                                     
"Burkholderia contaminans" = "Burkholderia",                                       
"Burkholderia multivorans" = "Burkholderia",                                       
"Burkhuldena cepacia" = "Burkholderia", 
"Burkolderia cepacia" = "Burkholderia",
"Burkoderia cepacia complex" = "Burkholderia",                                     
"Burkulderia Cepecia" = "Burkholderia",
"Burkholderia Cepacea Complex" = "Burkholderia",            
"Burkholderia Metalica " = "Burkholderia",                   
"Burkholderia Cepaciae Complex " = "Burkholderia",            
"Bukholderia Cepacia Complex" = "Burkholderia",              
"Burkholderia Cepacie Complex" = "Burkholderia",             
"Buurkholderia Cepacia Complex " = "Burkholderia",
"BUAKHOLDERIA  CEPACIA" = "Burkholderia",

"Bukholderia pseudomallei" = NA,

"BURICHOLDERIA CEPACIA " = "Burkholderia",

"PANDOSEA S/P" = "Pandoraea", 
"PANDORAEA S/P" = "Pandoraea",

"candida abricans" = "Candida spp.",
"CANDIDA GLABRATA" = "Candida spp.",
"CANDIDA ALBICANS" = "Candida spp.",
" Pichia kudriavzevii" = "Candida spp.",

"Chromobacterium violaceum" = "Chromobacterium",
"Chromobactrereium violaceum" = "Chromobacterium",
"Chryseobacterium arthosphaerae" = "Chryseobacterium",                             
"Chryseobacterium arthrosphaerae" = "Chryseobacterium",                            
"Chryseobacterium gleum" = "Chryseobacterium",                                     
"chryseobacterium indologenes" = "Chryseobacterium",                               
"Chryseobacterium indologenes" = "Chryseobacterium", 
"Chryseobacterium indologines" = "Chryseobacterium",
"Chryseobacterium Indologenes" = "Chryseobacterium",
"Chryseobacterium indolegenes" = "Chryseobacterium",
"Indologenes" = "Chryseobacterium",
"Chryseobacterium species" = "Chryseobacterium",                                   
"CHRYSEOBACTERIUM SPECIES" = "Chryseobacterium",                                   
"Chryseobacterium spp" = "Chryseobacterium",

"CITIOBACTER FREUNDII" = "Citrobacter",                                            
"citrobacter" = "Citrobacter",                                                     
"Citrobacter freundi" = "Citrobacter",                                             
"Citrobacter freundii" = "Citrobacter",                                            
"Citrobacter freundii complex" = "Citrobacter",                                    
"citrobacter fruendii" = "Citrobacter",
"Citrobacter freundii (CRE)" = "Citrobacter",
"Citrobacter koseri" = "Citrobacter",                                              
"Citrobacter Koseri" = "Citrobacter",                                              
"CITROBACTER KOSERI" = "Citrobacter",                                              
"Citrobacter koseri " = "Citrobacter",                                             
"Citrobacter species ( braakii)" = "Citrobacter",
"Citrobacter Species" = "Citrobacter",
"Citrobacter spp." = "Citrobacter",
"Citrobacter wrekmanii" = "Citrobacter",
"Citrobacter Braaki" = "Citrobacter",

"Clostridium innocuum" = "Clostridium",                                            
"Clostridium species" = "Clostridium",                                             
"clostridium tertium" = "Clostridium",                                             
"Clostridium tertium" = "Clostridium",    

"coagulase negative staphylococci" = "Coagulase-negative staphylococci (CoNS)",
"coagulase negative staphylococci (CONS)" = "Coagulase-negative staphylococci (CoNS)",
"Coagulase negative staphylococci (CONS)" = "Coagulase-negative staphylococci (CoNS)",
"Coagulase Negative Staphylococci (CONS)" = "Coagulase-negative staphylococci (CoNS)",
"coagulase negative staphylococcus" = "Coagulase-negative staphylococci (CoNS)",  
"Coagulase negative staphylococcus haemolyticus" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus coagulase negative" = "Coagulase-negative staphylococci (CoNS)",

"Comamonas kerstersii" = "Comamonas",                                              
"Comamonas testosteroni" = "Comamonas",                                            
"Comamonas testosteroni 2" = "Comamonas",                                          
"Comamonas testosteroni 3" = "Comamonas",                                          
"corynebacterium" = "Corynebacterium",                                             
"Corynebacterium amycolatum" = "Corynebacterium",  
"Corynebacterium afermentans" = "Corynebacterium",
"Corynebacterium jeikeium" = "Corynebacterium",                                    
"Corynebacterium pseudodiphtheriticum" = "Corynebacterium",                        
"Corynebacterium sp." = "Corynebacterium",                                         
"Corynebacterium species" = "Corynebacterium",                                     
"Corynebacterium spp" = "Corynebacterium",                                         
"Corynebacterium spp." = "Corynebacterium",                                        
"Corynebacterium stratium" = "Corynebacterium",                                    
"corynebacterium striatum" = "Corynebacterium",                                    
"Corynebacterium striatum" = "Corynebacterium",                                    
"Corynebacterium Striatum" = "Corynebacterium",                                    
"coynebacterium species " = "Corynebacterium",
"Corynebacterium propinquum" = "Corynebacterium",
"corynebecter striatum" = "Corynebacterium",
"CORYNEBACTERIUM RESISTENS" = "Corynebacterium", 

"Cronobacter sp." = "Cronobacter",                                                
"Cryptococcus laurentii" = "Cryptococcus",
"Cryptococcus neofarmans" = "Cryptococcus",
"Cutibacterium acnes" = "Cutibacterium", 
"Cupriavidus pauculus" = "Cupriavidus",

"Diphtheroids" = "Corynebacterium",                                                                     
"Edwardsiella tarda" = "Edwardsiella",                                                
"Eggerthella lenta " = "Eggerthella",
"Eggerthella lenta" = "Eggerthella",

"Elizabethkingia" = "Elizabethkingia",                                             
"Elizabethkingia miricola" = "Elizabethkingia",                                    
"Elizabethkingia anophelis" = "Elizabethkingia",                                   
"Elizabethkingia anophelis " = "Elizabethkingia",                                  
"Elizabethkingia meningoseptica" = "Elizabethkingia",                              
"ELIZABETHKINGIA SP." = "Elizabethkingia",                                         
"Elizabethkingia species" = "Elizabethkingia",                                     
"ELIZABETHKINGIA SPECIES" = "Elizabethkingia",                                     
"Elizabethkingid meningoseptica" = "Elizabethkingia",
"Elizabethkingia meningeseptica" = "Elizabethkingia",
"ELIZABERTKINGIA MENINGOSEPTICA" = "Elizabethkingia",
"Elizabethkingia spp" = "Elizabethkingia",
"Elizabethkingae meningoseptica" = "Elizabethkingia",

"Enterococcus faecium" = "Enterococcus spp.",                                           
"Enterococus faecium" = "Enterococcus spp.",
"Escherichia fergusonii" = "Escherichia",                                                         
"Flavobacterium" = "Flavobacterium",
"FUSOBACTERIUM" = "Fusobacterium", 
"FUSOBACTERIUM VARIUM" = "Fusobacterium",
"Fusobacterium species" = "Fusobacterium",                                         
"Gemella morbillorum" = "Gemella",                                                 
"GEMELLA SANGUINIS" = "Gemella",
"Gemella spp." = "Gemella",

"Granulicatella species" = "Granulicatella",                                          
"GROUP G STREPTOCOCCUS" = "Streptococcus",                                                           
"Haemophilus influenza" = "Haemophilus",                                           
"Haemophilus influenza " = "Haemophilus",                                          
"Haemophilus influenzae" = "Haemophilus",                                          
"Haemophilus Influenzae" = "Haemophilus", 
"Haemophylus influenzae" = "Haemophilus", 
"H.influenzae" = "Haemophilus",
"Haemophilus parainfluenza" = "Haemophilus",
"Halomonas (Alcaligenes) aquamarinus" = "Halomonas",

"Klebisela Oxitoca " = "Klebsiella",                                               
"KLEBISELA OXITOCA " = "Klebsiella",
"Klebsiella Oxytocae" = "Klebsiella",
"Klebisella aerogenes" = "Klebsiella",                                                
"klebisiella pneumonaie" = "K. pneumoniae",                                   
"Klebseilla aerogenes" = "Klebsiella",
"Kebsiella aerogenes" = "Klebsiella",
"Klebsiella" = "Klebsiella",                                                       
"Klebsiella  aerogenes" = "Klebsiella",                                            
"klebsiella  oxytoca"  = "Klebsiella",                                             
"klebsiella aerogenes" = "Klebsiella",                                             
"Klebsiella aerogenes" = "Klebsiella",                                             
"Klebsiella Aerogenes" = "Klebsiella",                                             
"KLEBSIELLA AEROGENES" = "Klebsiella",                                             
"Klebsiella aerogenes " = "Klebsiella",                                            
"Klebsiella aerogenes  "  = "Klebsiella",
"Kelbsiella aerogenes" = "Klebsiella",
"Klebsiella aerogenes (CRE, MDR)" = "Klebsiella",                                  
"Klebsiella aerogens" = "Klebsiella",                                              
"klebsiella aeroginosa" = "Klebsiella",                                            
"klebsiella arogenes" = "Klebsiella",                                              
"klebsiella oxytoca" = "Klebsiella",                                               
"Klebsiella oxytoca" = "Klebsiella",                                               
"Klebsiella Oxytoca" = "Klebsiella",
"K.oxytoca" = "Klebsiella",
"KLEBSIELLA OXYTOCA" = "Klebsiella",                                               
"Klebsiella oxytoca (CRE,MDR)" = "Klebsiella",                                     
"Klebsiella Ozaenae" = "Klebsiella",                                               
"Klebsiella pneumoniae (ESBL)" = "K. pneumoniae",                                
"Klebsiella species" = "Klebsiella",                                               
"Klebsiella Species" = "Klebsiella",                                               
"klebsiella spp" = "Klebsiella",                                                   
"Klebsiella Spp." = "Klebsiella",                                                  
"Klebsiella variicola" = "Klebsiella",
"Klebsiella(Enterobacter) aerugenes" = "Klebsiella",

"Kluyvera ascorbata" = "Kluyvera",                                                 
"Kluyvera intermedia" = "Kluyvera",                                                
"Kochuria kristinae" = "Kocuria",                                                 
"Kocuria kristinae" = "Kocuria",
"Kocuria rhizophila" = "Kocuria",

"Lactobacillus " = "Lactobacillus",
"Lactobacillus plantarum" = "Lactobacillus",
"Lactobacillus species" = "Lactobacillus",
"Leclercia adecaboxylata" = "Leclercia",                                           
"Leclercia adecarboxylata" = "Leclercia",                                          
"Leclercia adecarboxylate" = "Leclercia",                                          
"Leptotrichia wadei" = "Leptotrichia",                                                
"Leuconostoc" = "Leuconostoc",                                                     
"Leuconostoc lactis" = "Leuconostoc",                                              
"Leuconostoc species Abnormal " = "Leuconostoc",
"Leuconostoc species" = "Leuconostoc",
"Listeria monocytogenes" = "Listeria",

"macrococus species" = "Macrococcus",                                                 
"Methicilin Resistant Staphylococcus aureus" = "S. aureus",           
"Methicillin-resistant Staphylococcus aureus" = "S. aureus",          
"Methicillin-resistant Staphylococcus aureus (MRSA)" = "S. aureus",       
"Methicillin Resistant Staphyloccous haemolyticus" = "Coagulase-negative staphylococci (CoNS)",                                
"micrococcus luteus" = "Micrococcus",                                                
"Moraxella catarrhalis" = "Moraxella",                                            
"Moraxella cattarhalis" = "Moraxella",                                            
"Moraxella osloensis" = "Moraxella",                                              
"moraxella species" = "Moraxella",                                            
"Moraxella species" = "Moraxella", 
"Motaxella (Neisseria) ovis" = "Moraxella",
"Morganella morganii" = "Morganella",
"MRSA" = "S. aureus",
"Rapidly growing mycobacterium spp" = "Mycobacterium",

"Nakaseomces blabrata" = "Candida spp.",                                               
"Nakaseomyces (Candia) glabrata" = "Candida spp.",
"Nakaseomyces nivariensis" = "Candida spp.",

"NEISSERIA ELONGATA" = "Neisseria",                                               
"neisseria sicca" = "Neisseria",
"Neisseria mucosa" = "Neisseria",
"Nocardia cyriacigeorgica" = "Nocardia",

"Ochrobactrum anthropi" = "Ochrobactrum", 
"OCHROBACTRUM SPECIES" = "Ochrobactrum",
"Ochrobactrum intermedium" = "Ochrobactrum",

"Pandoraea species" = "Pandoraea",          
"pantoea agglomerans" = "Pantoea",                                                 
"Pantoea agglomerans" = "Pantoea",                                                 
"Pantoea Agglomerans" = "Pantoea",                                                 
"Pantoea agglumerans " = "Pantoea",                                                
"Pantoea dispersa" = "Pantoea",                                                    
"Pantoea species" = "Pantoea",                                                     
"PANTOEA SPP" = "Pantoea",                                                         
"Pantoea spp." = "Pantoea",
"Paraclostridium bifermentans" = "Paraclostridium",                                
"Pasteurella multocida" = "Pasteurella", 
"Pce" = NA, 
"Pediococcus acidilactici" = "Pediococcus",                                        
"Peptoniphilus asaccharolyticus" = "Peptoniphilus",                                
"Pluralibacter gergoviae" = "Pluralibacter",
"Plesiomonas shigollaoides" = "Plesiomonas",
"Prevotella denticola" = "Prevotella",                                                             
"Proteus hauseri" = "Proteus",                                                     
"Proteus mirabilis" = "Proteus",                                                   
"Proteus Mirabilis" = "Proteus",                                                   
"Proteus mirsbilis" = "Proteus",
"Protius Mirabilis" = "Proteus",

"Providencia rettgeri" = "Providencia",                                            
"PROVIDENCIA RETTGERI" = "Providencia",                                            
"Providencia rettigeri" = "Providencia",                                           
"Providencia Species" = "Providencia",                                             
"Providencia stuartii" = "Providencia", 

"Pseudomonas aeruginosa" = "Pseudomonas spp.",                                          
"Pseudomonas oryzihabitans" = "Pseudomonas spp.",                                       
"PSEUDONOMAS" = "Pseudomonas spp.",                                                     
"PSEUDONOMAS AERUGINOSA" = "Pseudomonas spp.",                                          
"Psudomonas aeruginosa" = "Pseudomonas spp.",                                           
"psudomonas punda" = "Pseudomonas spp.", 
"Pseudomonas putida" = "Pseudomonas spp.",

"Pluralibcter Gergoviae" = "Enterobacter",
"Enterobacter hormachei" = "Enterobacter",

"RALSTONIA INSIDIOSA" = "Ralstonia",
"Ralstonia mannitolilitica" = "Ralstonia",                                         
"Ralstonia mannitolilytica" = "Ralstonia",
"Ralstonia mannitolilytics" = "Ralstonia",
"Ralstonia picketti" = "Ralstonia",                                                
"Ralstonia pickettii" = "Ralstonia", 
"Raoultella ornithinolytica" = "Raoultella", 
"Raoultella terrigena" = "Raoultella",
"Raoulltella terrigena" = "Raoultella",
"RAOULTELLA PLANTICOLA" = "Raoultella",
"Rhizobium radiobacter" = "Rhizobium",                                             
"Roseomonas gilardii" = "Roseomonas",                                              
"Roseomonas mucosa" = "Roseomonas", 

"Salmonella serogroup D" = "Salmonella",

"serratia" = "Serratia",                                                           
"Serratia marcescens" = "Serratia",                                                
"SERRATIA MARCESCENS" = "Serratia",                                                
"Serratia marcescens " = "Serratia",                                               
"serratia marcesceus" = "Serratia",                                                
"Serratia mercescens" = "Serratia",                                                
"SERRATIA PLYMUTHICA" = "Serratia",                             
"Sphingmonas paucimobilis" = "Sphingomonas",                                       
"sphingomonas paucimobilis" = "Sphingomonas",                                      
"Sphingomonas paucimobilis" = "Sphingomonas",                                      
"Sphingomonas paucimobilis." = "Sphingomonas",
"Sphingomonas pseudosanguinis"  = "Sphingomonas",
"Sphingomos" = "Sphingomonas",                                                     
"STAHPHYLOCOCCUS EPIDEMIAL" = "Coagulase-negative staphylococci (CoNS)",
"Staphyloccocus Blanc" = "Staphylococcus",                                            
"Staphylococcus argenteus" = "Coagulase-positive staphylococcus (CoPS)",           
"Staphylococcus argentus" = "Coagulase-positive staphylococcus (CoPS)", 
"Staphylococcus Blanc" = "Staphylococcus",                                         
"Staphylococcus Blanc " = "Staphylococcus",
"Staphylococcus saprophyticus" = "Staphylococcus",
"STAPHYLOCOCCUS SAPROPHYTICUS" = "Staphylococcus",
"Stapphylococcus haemolyticus" = "Staphylococcus",
"Mammaliicoccus (Staphylococcus) sciuri" = "Mammaliicoccus",

"staphylococcus capitis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus capitis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus Capitis" = "Coagulase-negative staphylococci (CoNS)",
"STAPHYLOCOCCUS CAPITIS" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus capitis " = "Coagulase-negative staphylococci (CoNS)",

"Staphylococcus Capitis & miccocus luteus" = NA, 

"staphylococcus caprae" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus coagulase-negative" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus cohnii" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus epidermidis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus Epidermidis" = "Coagulase-negative staphylococci (CoNS)",
"STAPHYLOCOCCUS EPIDERMIDIS" = "Coagulase-negative staphylococci (CoNS)",
"STAPHYLOCOCCUS EPIDERMIS (X2 SITES)" = "Coagulase-negative staphylococci (CoNS)",
"staphylococcus epidermis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus epidermis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus Epidermis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus Epidermis " = "Coagulase-negative staphylococci (CoNS)",
"staphylococcus haemolyticus" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus haemolyticus" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus haemolyticus " = "Coagulase-negative staphylococci (CoNS)",
"Stapphylococcus haemolyticus" = "Coagulase-negative staphylococci (CoNS)",

"STAPHYLOCOCCUS HAEMOLYTICUS, Corynebacterium species" = NA,

"staphylococcus hominis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus hominis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus hominis " = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus hominis (x 2sites)" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus hemolyticus" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus lugdunensis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus Lugdunensis" = "Coagulase-negative staphylococci (CoNS)",
"Staphylococcus saphrophyticus" = "Coagulase-negative staphylococci (CoNS)",

"Staphylococcus species" = "Staphylococcus",                                      
"Staphylococcus spp" = "Staphylococcus",                                           
"Staphylococcus warneri" = "Coagulase-negative staphylococci (CoNS)",              
"Stenomaltophila" = "Stenotrophomonas spp.",                                            
"Stenotrophomonas maltophilia" = "Stenotrophomonas spp.",
"stenoprophomonas maltopilia" = "Stenotrophomonas spp.",

"Flavimonas oryzihabitans" = "Pseudomonas spp.",

"Steptococcus pyogenes" = "Streptococcus",                                         
"steptococus gallolyticuc" = "Streptococcus",                                      
"steptococus pyogenes (strep.group A)" = "Streptococcus",                          
"streptococcus agalactiae" = "Streptococcus",                                      
"Streptococcus agalactiae" = "Streptococcus",                                      
"Streptococcus agalactiae (Group B)" = "Streptococcus",
"Streptococcus agalactica Group B" = "Streptococcus",
"GROUP B STREPTOCOCCUS" = "Streptococcus",
"Streptococcus anginosus" = "Streptococcus",                                       
"streptococcus Anginosus " = "Streptococcus",                                      
"Streptococcus angnosus " = "Streptococcus",                                       
"Streptococcus dyagalactiae" = "Streptococcus",                                    
"Streptococcus Dysagalactiae" = "Streptococcus",                                   
"streptococcus dysgalactiae" = "Streptococcus",                                    
"Streptococcus dysgalactiae" = "Streptococcus",                                   
"streptococcus gallolyticus spp pasteurianus" = "Streptococcus",       
"Streptococcus gallolyticus spp pasteurianus" = "Streptococcus",                   
"Streptococcus gordonii" = "Streptococcus",                                        
"Streptococcus Group D" = "Streptococcus",                                         
"Streptococcus infantarius" = "Streptococcus",                                     
"Streptococcus mitis" = "Streptococcus",                                           
"STREPTOCOCCUS MITIS GROUP" = "Streptococcus",                                     
"STREPTOCOCCUS MITIS GROUP " = "Streptococcus",                                    
"streptococcus mitis/ozalis" = "Streptococcus",                                    
"Streptococcus mitis/streptococcus oralis" = "Streptococcus", 
"Streptococcus Mileri " = "Streptococcus",
"Streptococcus oralis" = "Streptococcus",                                          
"Streptococcus pneumoniae" = "S. pneumoniae",                                      
"streptococcus pseudoporcinus" = "Streptococcus",                                  
"Streptococcus pyogenes" = "Streptococcus",
"Streptococcus pyogens " = "Streptococcus",
"streptococcus sanglinis" = "Streptococcus",                                       
"Streptococcus species" = "Streptococcus", 
"Streptococcus salivarius group" = "Streptococcus", 
"Streptococcus vestibularis" = "Streptococcus",                                    
"streptococus angionosus" = "Streptococcus",
"Streptococcus acidominimus" = "Streptococcus",
"Streptocoocus gordonii" = "Streptococcus",
"Streptococcus anginosus group" = "Streptococcus",
"Streptococcus constellatus " = "Streptococcus",
"Streptococcus gallolyticus" = "Streptococcus",

"Shewanella algae " = "Shewanella",
"Shewanella putrefaciens" = "Shewanella",

"TRACHEAL ASPIRATE" = NA,   
"Trichosporn species" = "Trichosporon",                                            
"Trichosporon asahii" = "Trichosporon",                                            
"TRICHOSPORON ASAHII" = "Trichosporon",                                            
"Veillonella parvula" = "Veillonella",                                             
"WEISSELLA CONFUSA" = "Weissella",
"Weisella confusa " = "Weissella",
".Burkholderia cepacia complex" = "Burkholderia",
" " = NA,

"Enterococcus gallinarum" = "Enterococcus spp.",
"Clostridium clostridioforme" = "Clostridium",               
"Enterobacter aerogenes" = "Enterobacter",                    
"Oligotrophomonas maltophilia" = "Stenotrophomonas spp.",
"Enterococcus raffinosus" = "Enterococcus spp.",                  
"Sma" = "Stenotrophomonas spp.",
"Alcaligenes xylosoxidans" = "Alcaligenes",                  
"Elizabethia anopheles" = "Elizabethkingia",
"Achromobacter xyloxide" = "Achromobacter",                    
"Hydrostreptococcus gallate" = "Streptococcus",
"Elizabethobacteria meningosepticum" = "Elizabethkingia",         
"Staphylococcus capitiy is cap" = "Coagulase-negative staphylococci (CoNS)",
"Enterobacter cloacae" = "Enterobacter",                      
"Chrysebacterium indolegenes " = "Chryseobacterium",
"PANTOEA " = "Pantoea",                                  
"Staphylococus epidermidis" = "Coagulase-negative staphylococci (CoNS)",
"Aspeergillus fumigatus " = "Aspergillus",                   
"Serratia marcesenes " = "Serratia",
"Burkholderia cepecia " = "Burkholderia",                     
"Sphingomonas morbilis " = "Sphingomonas",
"Staphylococus capitis " = "Coagulase-negative staphylococci (CoNS)",                  
"S.epidermidis" = "Coagulase-negative staphylococci (CoNS)", 
"Aeromonas verroni" = "Aeromonas",                         
"Burkholderia cepaciae" = "Burkholderia",
"acinetobacter baumanii" = "Acinetobacter spp.",                    
"acinetobacter spp" = "Acinetobacter spp.", 
"acinetobacter baumini" = "Acinetobacter spp.",                       
"Corynebacterium arthrosphaerae" = "Corynebacterium",
"Staphylococcus sp." = "Staphylococcus",                        
"Triochosporan asahii" = "Trichosporon",
"Burkholderia SPP." = "Burkholderia",                         
"Bacilius SP." = "Bacillus",
"Staphylococcud lugdunensis" = "Coagulase-negative staphylococci (CoNS)",                 
"Burkholderia gladioli" = "Burkholderia",
"Nakaseomyces glabratus" = "Candida spp.",                   
"ARCANOBACTERIUM HAEMOLYTICUM" = "Arcanobacterium",
"Burkholderia vietnamiensis" = "Burkholderia",                
"Streptococcus sanguinis" = "Streptococcus",
"Streptococcus mitis/oralis" = "Streptococcus",                
"Salmonella enterica" = "Salmonella",
"Elizabethkinglia anophelis" = "Elizabethkingia",                
"Pantoea sp" = "Pantoea",
"Achromobacter xylosoxidans ss denitrificans" = "Achromobacter",
" Elizabethkingia meningosepticum" = "Elizabethkingia",
"Diptheroids" = "Corynebacterium",                               
"Elizabethkingia meningosepticum" = "Elizabethkingia",
"Aerococccus spp" = "Aerococcus",                           
"Burholderia gladioli" = "Burkholderia",
"Trichosporon spp." = "Trichosporon",                         
"Nakaseomyces glabrata" = "Candida spp.", 
"Halomonas aquamarinus" = "Halomonas",                     
"Plesiomonas shigelloides" = "Plesiomonas",
"Chryseobacterium taklimakanense" = "Chryseobacterium",            
"Stenotrophomomas maltophilia" = "Stenotrophomonas spp.",
"Brevibacterium casei" = "Brevibacterium",                      
"Ralstomia mannitolilytica" = "Ralstonia",
"Bactericides uniformis" = "Bacteroides",

"candida paratropicalis" = "Candida spp.",
"streptococcus sanguis" = "Streptococcus",
"streptococus,agalactiae" = "Streptococcus",            
"Enterococcus faecalis" = "Enterococcus spp.",
"Citrobacter koserii" = "Citrobacter",                
"ROSEMONAS GIRRDII" = "Roseomonas",
"Corynebacterium bovis" = "Corynebacterium",              
"Geotrichum SP." = "Geotrichum",
"Bacillus sp." = "Bacillus",                       
"Burkhoderia cepacia " = "Burkholderia",
"S. epidermidis" = "Coagulase-negative staphylococci (CoNS)",                     
"Delftia acidovorans" = "Delftia",
"Comamonas testosteronii" = "Comamonas",             
"Klebsiella (Enterobacter) aerogenes " = "Klebsiella",
"Yeast cell" = "Candida spp.",                         
"Pleiseomonas shigelloides" = "Plesiomonas",
"Klebsiella oxytocin" = "Klebsiella",

"Streptococcus constellation" = "Streptococcus",
"Fusobacterium nucleatum" = "Fusobacterium",   
"Klebsiella acidogenes" = "Klebsiella",      
"Lactobacillus fermentans" = "Lactobacillus",   
"Human Staphylococcus" = "Staphylococcus",                 
"staphylococcus aureus" = "S. aureus",     
"N0" = NA,   
"Cryseobacterium indologenes" = "Chryseobacterium",
"Kalamiella piersonii" = "Kalamiella",       
"Burkholderia seminalis" = "Burkholderia",   
"Ochrobacrum anthropi" = "Ochrobactrum",      
"Streptococcus viridans" = "Streptococcus",     
"Burkholderia gladiola" = "Burkholderia",
"Myroides sp." = "Myroides",
"Yeast" = "Unspecified fungus"
)

# 
cleaned_mapping <- setNames(lapply(names(name_mapping), function(key) {
  trimws(key, which = "both")
}), name_mapping)

standardize_org_name <- function(name, mapping) {
  # Normalize the name by removing all extra spaces and converting to lower case
  normalized_name <- tolower(gsub("[[:punct:]]", "", gsub("[[:space:]]+", " ", str_trim(name))))
  
  # Match the normalized name against patterns in the mapping, allowing for extra characters
  matches <- sapply(names(mapping), function(pattern) {
    # Normalize pattern for matching
    normalized_pattern <- tolower(gsub("[[:punct:]]", "", gsub("[[:space:]]+", " ", trimws(pattern))))
    grepl(paste0("^", normalized_pattern, "$"), normalized_name)
  })
  
  # If a match is found, return the mapped value; otherwise, return the original name
  if (any(matches)) {
    return(mapping[names(mapping)[which(matches)[1]]])
  } else {
    return(name)
  }
}

ast_add <- ast_add %>%
  mutate(org_names_all = sapply(org_names_all, standardize_org_name, mapping = name_mapping))

# Updated lists of organism names for each class
# Gram-negative bacteria (gnb_list)
gnb_list <- c("Pseudomonas spp.", "Shewanella", "Acinetobacter spp.", "E. coli", "Sphingomonas", 
              "Haemophilus", "K. pneumoniae", "Burkholderia", "Klebsiella", "Pantoea", 
              "Chromobacterium", "Ochrobactrum", "Elizabethkingia", "Enterobacter", 
              "Aeromonas", "Pandoraea", "Citrobacter", "Stenotrophomonas spp.", "Morganella", 
              "Serratia", "Proteus", "Kluyvera", "Achromobacter", "Providencia", 
              "Chryseobacterium", "Raoultella", "Ralstonia", "Moraxella", "Neisseria", 
              "Prevotella", "Cupriavidus", "Flavobacterium", "Leclercia", 
              "Pluralibacter", "Roseomonas", "Agrobacterium", "Rhizobium", 
              "Halomonas", "Comamonas", "Edwardsiella", "Plesiomonas", "Cronobacter", 
              "Pasteurella", "Salmonella", "Escherichia", "Veillonella",
              "Alcaligenes", "Delftia", "Bacteroides", "Fusobacterium", "Leptotrichia",
              "Kalamiella", "Myroides")

# Gram-positive bacteria (gpb_list)
gpb_list <- c("Coagulase-negative staphylococci (CoNS)", "S. aureus", 
              "S. pneumoniae", "Enterococcus spp.", "Streptococcus", 
              "Corynebacterium", "Pediococcus", "Lactobacillus", "Actinomyces", 
              "Anaerococcus", "Peptoniphilus", "Kocuria", "Cutibacterium", 
              "Coagulase-positive staphylococcus (CoPS)", "Bacillus", "Micrococcus", 
              "Macrococcus", "Nocardia", "Aerococcus", "Granulicatella", "Leuconostoc", 
              "Clostridium", "Paraclostridium", "Eggerthella",  "Abiotrophia", 
              "Weissella", "Gemella", "Arthrobacter", "Listeria", 
              "Mycobacterium", "Mammaliicoccus", 
              "Staphylococcus", "Arcanobacterium", "Brevibacterium")

# Fungi (fungi_list)
fungi_list <- c("Candida spp.", "Cryptococcus", "Aspergillus", "Trichosporon", "Bipolaris", "Geotrichum", "Unspecified fungus")

# Check for unclassified microorganisms
remaining_orgs <- setdiff(unique(ast_add$org_names_all), c(gnb_list, gpb_list, fungi_list))

# Output unclassified microorganisms
remaining_orgs

# Adding a new column 'Class' based on 'org_names_all'
ast_add <- ast_add %>%
  mutate(Class = case_when(
    org_names_all %in% gnb_list ~ "GNB",
    org_names_all %in% gpb_list ~ "GPB",
    org_names_all %in% fungi_list ~ "Fungi",
    TRUE ~ "Unknown"   
  ))

# Combine
ast_results <- cbind(ast_results, ast_add)
ast_results <- as.data.frame(ast_results)

anti_used <- anti %>%
  arrange(anti_group)

# AST related variables
ast_used <- ast_results[,c(which(colnames(ast_results) %in% c(anti_used$sus_names, names(ast_add))))]

# Trans to factor
anti_used$anti_group <- factor(trimws(as.character(anti_used$anti_group)))

###
# Order anti_used$sus_names ("susceptibility_")
match_order <- match(anti_used$sus_names, colnames(ast_used))
ast_add_index <- which(colnames(ast_used) %in% names(ast_add))
match_order <- c(match_order, ast_add_index) 

# New order
ast_used <- ast_used[, match_order]
colnames(ast_used) <- c(anti_used$anti_names, names(ast_add))

# Update org based on others 
ast_used <- ast_used %>%
  mutate(
    org = case_when(
      org == 14 & org_names_all == "E. coli" ~ 1,
      org == 14 & org_names_all == "K. pneumoniae" ~ 2,
      org == 14 & org_names_all == "Acinetobacter spp." ~ 3,
      org == 14 & org_names_all == "Pseudomonas spp." ~ 4,
      org == 14 & org_names_all == "Serratia" ~ 5,
      org == 14 & org_names_all == "Proteus" ~ 6,
      org == 14 & org_names_all == "Morganella" ~ 7,
      org == 14 & org_names_all == "Enterobacter" ~ 8,
      org == 14 & org_names_all == "Stenotrophomonas spp." ~ 9,
      org == 14 & org_names_all == "S. aureus" ~ 10,
      org == 14 & org_names_all == "Enterococcus spp." ~ 11,
      org == 14 & org_names_all == "S. pneumoniae" ~ 12,
      org == 14 & org_names_all == "Candida spp." ~ 13,
      org == 14 & is.na(org_names_all) ~ NA_real_,
      TRUE ~ org 
    )
  )

# -----------------------------------------------------------------------
# Carbapenem resistance 
# Certapenem-resistant Acinetobacter / Pseudomonas should NOT be considered CRAB / CR-PA 
# because both Acinetobacter and Pseudomonas are intrinsically resistant to ertapenems
# Trans all AST results to NA
pa_ab_index <- which(ast_used$org_names_all %in% c("Acinetobacter spp.", "Pseudomonas spp."))
ast_used$Ertapenem[pa_ab_index] <- 5

# -----------------------------------------------------------------------
# For Acinetobacter (anti: Ampicillin/sulbactam)
# intrinsically resistant to Amoxicillin-clavulanate and Cefotaxime/clavulanic acid
ab_spp_index <- which(ast_used$org_names_all == "Acinetobacter spp.")
ast_used$`Amoxicillin-clavulanate`[ab_spp_index] <- 5
ast_used$`Cefotaxime/clavulanic acid`[ab_spp_index] <- 5

# -----------------------------------------------------------------------
# Polymyxins are ineffective against Providencia spp., Neisseria spp., 
# Proteus spp., Serratia marcescens, and Burkholderia cepacia
polymyxins_R_org_index <- which(ast_used$org_names_all %in% c("Burkholderia", "Morganella", "Serratia", "Proteus", "Providencia", "Neisseria", "Veillonella", "Clostridium", "Bacteroides", "Fusobacterium", "Mycobacterium", "Kalamiella", "Myroides", "Staphylococcus", "Enterococcus spp.", "Prevotella", "Actinomyces", "Paraclostridium", "Cutibacterium"))

# Specific antibiotics for Polymyxins
polymyxins_spec_anti_cols <- which(colnames(ast_used) %in% anti$anti_names[anti$anti_group == "Polymyxins"])

# Trans all AST results to NA
ast_used[polymyxins_R_org_index, polymyxins_spec_anti_cols] <- 5
# -----------------------------------------------------------------------
## Prepare different graphics
# Split anti group
df_anti_used <- split(anti_used, anti_used$anti_group)

process_ast_group <- function(df_anti_used_group, ast_used) {
  df_ast_ori <- df_ast <- ris <- ast_merged <- list()
  
  system.time({
    for (i in seq_along(df_anti_used_group)) {
      df <- df_anti_used_group[[i]]
      df_ast_ori[[i]] <- ast_used %>% select(df$anti_names)
      ris[[i]] <- apply(df_ast_ori[[i]], 1, min)
    }
  })
  
  for (i in seq_along(df_ast_ori)) {
    # Initialize df_ast[[i]] with the structure of df_ast_ori[[i]]
    df_ast[[i]] <- df_ast_ori[[i]]
    
    for (j in 1:nrow(df_ast_ori[[i]])) {
      df_ast[[i]][j, ] <- ifelse(df_ast[[i]][j, ] == ris[[i]][j], 1, 0)
    }
    
    ast_merged[[i]] <- cbind(df_ast_ori[[i]], ris[[i]])
    colnames(ast_merged[[i]]) <- c(colnames(df_ast_ori[[i]]), paste0("ris_", names(df_anti_used_group)[i]))
  }
  
  return(list(df_ast_ori = df_ast_ori, df_ast = df_ast, 
              ris = ris, ast_merged = ast_merged))
}

results_ast <- process_ast_group(df_anti_used, ast_used)

# Extract results 
df_ast <- results_ast$df_ast_ori
ris_all <- results_ast$ris
ast_merged <- results_ast$ast_merged

# ---------------
# Merge organisms
# levels 1 to 5, 9 to 11, 13 respectively represent 
# "E. coli", "K. pneumoniae","Acinetobacter spp.", "Pseudomonas spp.",
# "Serratia/Proteus/Morganella/Enterobacter"
# "Stenotrophomonas spp.", "S. aureus", "Enterococcus spp.", "Candida spp."
# 14 others
###
# Each ast and other info
process_each_ast <- function(ast_merged, ast_used, ast_add_index) {
  each_ast <- list()
  
  for (i in seq_along(ast_merged)) {
    each_ast[[i]] <- cbind(ast_merged[[i]], ast_used[, ast_add_index])
    
    each_ast[[i]] <- each_ast[[i]] %>%
      mutate(
        org_new = case_when(
          org %in% c(1, 2, 3, 4, 9, 10, 11, 13, 14) ~ org,
          org %in% c(5, 6, 7, 8) ~ 5,
          org %in% 12 ~ 14,
          TRUE ~ NA_real_
        )
      )
    
    each_ast[[i]]$pathogen_group <- case_when(
      each_ast[[i]]$org_new %in% c("1", "2", "3", "4", "5", "9") ~ "GNB",
      each_ast[[i]]$org_new %in% c("10", "11") ~ "GPB",
      each_ast[[i]]$org_new %in% c("13") ~ "Fungi",
      TRUE ~ NA_character_
    )
  }
  
  return(each_ast)
}

#
each_ast <- process_each_ast(ast_merged, ast_used, ast_add_index)

# Combine all ast data into one single data frame
all_ast_merged <- do.call(cbind, ast_merged)

# Add other info
all_ast_merged <- cbind(all_ast_merged, ast_used[, ast_add_index])

# Add AST results for methicillin
methicillin_cols <- c("Oxacillin", "Cefoxitin", "Cefazolin", "Cloxacillin")
all_ast_merged$Methicillin <- apply(all_ast_merged[, methicillin_cols], 1, min, na.rm = TRUE)

# Combine organisms into new group
all_ast_merged <- all_ast_merged %>% 
  mutate(
    org_new = case_when(
      org %in% c(1, 2, 3, 4, 9, 10, 11, 13, 14) ~ org,
      org %in% c(5, 6, 7, 8) ~ 5,
      org %in% 12 ~ 14,
      TRUE ~ NA_real_
    )
  )

# Add pathogen group for new group of listed organisms
all_ast_merged$pathogen_group <- case_when(
    all_ast_merged$org_new %in% c("1", "2", "3", "4", "5", "9") ~ "GNB",
    all_ast_merged$org_new %in% c("10", "11") ~ "GPB",
    all_ast_merged$org_new %in% c("13") ~ "Fungi",
    TRUE ~ NA_character_
  )

# Trans organism names
all_ast_merged$org_new <- factor(all_ast_merged$org_new,
                                 levels = c(1:5, 9:11, 13, 14),
                                 labels = c("E. coli", "K. pneumoniae", 
                                            "Acinetobacter spp.", "Pseudomonas spp.", 
                                            "Serratia/Proteus/Morganella/Enterobacter",
                                            "Stenotrophomonas spp.", "S. aureus",
                                            "Enterococcus spp.", "Candida spp.", "Others"))
# ------------------------------------------------------------------------------------
# Revise AST results for CRE & 3GCRE
# Specific antibiotics for carbapenem or third-generation cephalosporins
car_anti_cols <- which(colnames(all_ast_merged) %in% c(anti$anti_names[anti$anti_group == "Carbapenem" | anti$anti_group_pa_ab == "Carbapenem"], "ris_Carbapenem"))


tgc_anti_cols <- which(colnames(all_ast_merged) %in% c(anti$anti_names[anti$anti_group == "Third-generation cephalosporin" | anti$anti_group_pa_ab == "Third-generation cephalosporin"], "ris_Third-generation cephalosporin"))

# Enterobacterales
ent_spec_org <- c(
  "E. coli", "K. pneumoniae", "Klebsiella", 
  "Enterobacter", "Serratia", "Proteus", "Morganella",
  "Citrobacter", "Providencia", "Raoultella", "Kluyvera",
  "Cronobacter", "Leclercia", "Pluralibacter", 
  "Edwardsiella", "Pantoea", "Escherichia", "Salmonella",
  "Kalamiella"
)

rows_ent_ast_all <- which(all_ast_merged$org_names_all %in% ent_spec_org)

# CRE
rows_car_r_all <- which(all_ast_merged$ris_Carbapenem == 1)
rows_cre_ent_r_all <- intersect(rows_ent_ast_all, rows_car_r_all)

all_ast_merged[rows_cre_ent_r_all, tgc_anti_cols] <- 5 # 3GC to NA

# 3GCRE
rows_car_other_all <- which(all_ast_merged$ris_Carbapenem != 1)
rows_3gcre_r_all_ori <- which(all_ast_merged$`ris_Third-generation cephalosporin` == 1)

rows_3gcre_r_all <- intersect(rows_car_other_all, rows_3gcre_r_all_ori)
all_ast_merged[rows_3gcre_r_all, car_anti_cols] <- 5 # CR to NA

# ------------------------------------------------------------------------------------
# Index episode and related organisms
all_ast_merged_index_vap <- all_ast_merged[which(all_ast_merged$f07m_vapc == 1),]
all_ast_merged_index_bsi <- all_ast_merged[which(all_ast_merged$f07m_bsic == 1),]

# Delete some error organisms recorded more than one time in the same episode
all_ast_merged_index_vap <- all_ast_merged_index_vap %>%
  group_by(recordid, org_names_all) %>%
  distinct(recordid, org_names_all, .keep_all = TRUE) %>%
  ungroup()

all_ast_merged_index_bsi <- all_ast_merged_index_bsi %>%
  group_by(recordid, org_names_all) %>%
  distinct(recordid, org_names_all, .keep_all = TRUE) %>%
  ungroup()

# Combine data
all_ast_merged_index <- rbind.data.frame(all_ast_merged_index_vap, all_ast_merged_index_bsi)
###
```
# Infection types for duplicate recordid
```{r}
# For those with same infection onset of VAP and BSI
duplicate_all_ast_merged_index <- all_ast_merged_index[which(all_ast_merged_index$recordid %in% duplicate_recordids), ]

# If there are occurring the different organisms in both VAP and BSI episode, included respectively into VAP and BSI
different_org_records <- duplicate_all_ast_merged_index %>%
  group_by(recordid) %>%
  filter(any(f07m_vapc == 1) & any(f07m_bsic == 1)) %>%
  filter(n_distinct(org_names_all) > 1) %>%
  ungroup()

same_org_records <- duplicate_all_ast_merged_index %>%
  group_by(recordid) %>%
  filter(any(f07m_vapc == 1) & any(f07m_bsic == 1)) %>%
  filter(n_distinct(org_names_all) == 1) %>%
  ungroup()

# Based on the earlier infection onset date
all_ast_merged_index_remain <- all_ast_merged_index[-which(all_ast_merged_index$recordid %in% duplicate_rows$recordid),]

# Combine all dataframes related to all_ast_merged_index
all_ast_merged_index <- rbind.data.frame(all_ast_merged_index_remain, same_org_records, different_org_records)
```
# Infection types with and without the duplicate 
```{r}
# -------------------------------------
# To choose the earlier infection onset
recordid_not_duplicate <- combined_df_ori %>%
  filter(!recordid %in% duplicate_rows$recordid) %>% 
  arrange(recordid, inf_onset) %>% 
  group_by(recordid) %>% 
  slice(1) 

# -------------------------------------
# For those including duplicate_rows with same organisms
same_org_duplicate_rows <- combined_df_ori %>%
  filter(recordid %in% same_org_records$recordid) %>% 
  filter(infection_types == "VAP")

# -------------------------------------
# For those including duplicate_rows with different organisms
diff_org_duplicate_rows <- combined_df_ori %>%
  filter(recordid %in% different_org_records$recordid)  
  
# --------------------------------------
# Combine
inf_add <- rbind.data.frame(recordid_not_duplicate, same_org_duplicate_rows, diff_org_duplicate_rows)

# Trans format
inf_add$inf_onset <- as.Date(inf_add$inf_onset, format="%Y-%m-%d")
```
# Modify recordid for those with VAP and BSI in ind_add
```{r}
# recordid of those with VAP and BSI
inf_add_duplicated_rows <- which(duplicated(inf_add$recordid) | duplicated(inf_add$recordid, fromLast = TRUE))

inf_add_revise_id <- unique(inf_add$recordid[inf_add_duplicated_rows])

# recordid_with_suffix are added based on the presence of substrings in infection_types
inf_add$recordid[inf_add_duplicated_rows] <- with(inf_add[inf_add_duplicated_rows,], {
  ifelse(grepl("VAP", infection_types), 
         paste0(recordid, "_VAP"), 
         ifelse(grepl("BSI", infection_types), 
                paste0(recordid, "_BSI"), 
                recordid))
})
```
# Modify recordid of each_ast[[i]] and all_ast_merged_index
# Add infection types
```{r}
# Define the function
process_ast_data <- function(ast_data, inf_add, recordid_not_duplicate, same_org_duplicate_rows, diff_org_duplicate_rows) {
  # Filter 'ast_data' based on 'recordid_not_duplicate'
  filtered_records_not_duplicate <- ast_data %>%
    filter(recordid %in% recordid_not_duplicate$recordid)
  
  # Get record IDs from inf_add based on infection types
  inf_add_has_vap_id <- inf_add %>%
    filter(str_detect(infection_types, "VAP")) %>%
    pull(recordid)
  
  inf_add_has_bsi_id <- inf_add %>%
    filter(str_detect(infection_types, "BSI")) %>%
    pull(recordid)
  
  # Filter for VAP and BSI cases
  filtered_records_not_duplicate_vap <- filtered_records_not_duplicate %>%
    filter(recordid %in% inf_add_has_vap_id, f07m_vapc == 1)
  
  filtered_records_not_duplicate_bsi <- filtered_records_not_duplicate %>%
    filter(recordid %in% inf_add_has_bsi_id, f07m_bsic == 1)
  
  # Combine the filtered records
  filtered_records_not_duplicate <- bind_rows(filtered_records_not_duplicate_vap, filtered_records_not_duplicate_bsi)
  
  # Filter rows in 'ast_data' where 'recordid' is in 'same_org_duplicate_rows'
  # Only keep rows where f07m_vapc == 1
  filtered_same_org <- ast_data %>%
    filter(recordid %in% same_org_duplicate_rows$recordid, f07m_vapc == 1)
  
  # Filter rows in 'ast_data' where 'recordid' is in 'diff_org_duplicate_rows'
  filtered_diff_org <- ast_data %>%
    filter(recordid %in% diff_org_duplicate_rows$recordid)
  
  # Function to modify recordid based on conditions
  modify_recordid <- function(df) {
    df$recordid <- as.character(df$recordid)
    
    # Initialize empty lists to store modified data frames
    df_vap <- data.frame()
    df_bsi <- data.frame()
    
    # Get unique recordids
    unique_records <- unique(df$recordid)
    
    # Loop through each unique recordid
    for (rec_id in unique_records) {
      # Subset the data frame for the current recordid
      subset_df <- df[df$recordid == rec_id, ]
      
      # Check and handle f07m_vapc condition
      if (any(subset_df$f07m_vapc == 1)) {
        df_vap_temp <- subset_df
        df_vap_temp$recordid <- paste0(rec_id, "_VAP")
        df_vap <- rbind(df_vap, df_vap_temp)
      }
      
      # Check and handle f07m_bsic condition
      if (any(subset_df$f07m_bsic == 1)) {
        df_bsi_temp <- subset_df
        df_bsi_temp$recordid <- paste0(rec_id, "_BSI")
        df_bsi <- rbind(df_bsi, df_bsi_temp)
      }
    }
    
    # Combine the results from both conditions
    df_modified <- rbind(df_vap, df_bsi)
    
    return(df_modified)
  }
  
  # Apply the function to your dataframe
  modified_diff_org <- modify_recordid(filtered_diff_org)
  
  modified_diff_org_vap <- modified_diff_org %>%
    filter(str_detect(recordid, "_VAP$") & f07m_vapc == 1)
  
  modified_diff_org_bsi <- modified_diff_org %>%
    filter(str_detect(recordid, "_BSI$") & f07m_bsic == 1)
  
  modified_diff_org <- bind_rows(modified_diff_org_vap, modified_diff_org_bsi)
  
  # Combine data
  all_ast_combined <- bind_rows(filtered_records_not_duplicate,
                                filtered_same_org, modified_diff_org)
  
  # Add infection types
  all_ast_combined <- left_join(all_ast_combined, inf_add, by = "recordid")
  
  return(all_ast_combined)
}

# Usage for all_ast_merged_index
all_ast_merged_index <- process_ast_data(all_ast_merged_index, inf_add, recordid_not_duplicate, same_org_duplicate_rows, diff_org_duplicate_rows)

# --------------------
# Define custom function to calculate min with a check for missing values, ensuring the return type is Date
custom_min <- function(x) {
  x <- as.Date(x)
  if (length(x) == 0L || all(is.na(x))) {
    NA_Date_    # as NA          
  } else {
    suppressWarnings(min(x, na.rm = TRUE))
  }
}

# Apply custom_min function to Index Specimen Date
spec_date_index <- all_ast_merged_index %>%
  group_by(recordid) %>%
  dplyr::summarize(spec_date = custom_min(spec_date), ast_date = custom_min(ast_date), .groups = "keep") %>%
  ungroup()

# Replace NA in inf_onset with spec_date for matching recordid
inf_add <- inf_add %>%
  left_join(spec_date_index[, c("recordid", "spec_date")], by = "recordid") %>%
  mutate(inf_onset = as.Date(ifelse(is.na(inf_onset), spec_date, inf_onset), origin = "1970-01-01")) %>%
  select(-spec_date)

# --------------------
# Usage for each element in each_ast
process_each_ast_list <- function(each_ast_list, inf_add, recordid_not_duplicate, same_org_duplicate_rows, diff_org_duplicate_rows) {
  lapply(each_ast_list, function(ast) {
    process_ast_data(ast, inf_add, recordid_not_duplicate, same_org_duplicate_rows, diff_org_duplicate_rows)
  })
}
# Apply the processing to each ast group
each_ast <- process_each_ast_list(each_ast, inf_add, recordid_not_duplicate, same_org_duplicate_rows, diff_org_duplicate_rows)
```
# Modify recordid for those with VAP and BSI in all dataframe 
```{r}
# --------------------
# One row per patients
# data[[1]], data[[3]], data[[4]], data[[7]], data[[8]]
cols_to_modify <- c(1, 3, 4, 7, 8)

for (col in cols_to_modify) {

  rows_to_modify <- data[[col]] %>%
    filter(recordid %in% inf_add_revise_id)
  
  rows_unmodified <- data[[col]] %>%
    filter(!(recordid %in% inf_add_revise_id))
  
  rows_VAP <- rows_to_modify %>%
    mutate(recordid = paste0(recordid, "_VAP"))
  
  rows_BSI <- rows_to_modify %>%
    mutate(recordid = paste0(recordid, "_BSI"))
  
  data[[col]] <- bind_rows(rows_unmodified, rows_VAP, rows_BSI)
}

# -------------------
# data[[2]]
# Filter the data for redcap_repeat_instance == 1
data_2_index <- data[[2]][data[[2]]$redcap_repeat_instance == 1,]

# Split the data into VAP and BSI episodes
data_2_index_vap <- data_2_index[data_2_index$redcap_event_name == "vap_episode_arm_1",]
data_2_index_bsi <- data_2_index[data_2_index$redcap_event_name == "bsi_episode_arm_1",]

# Update record IDs for VAP episodes
data_2_index_vap$recordid[data_2_index_vap$recordid %in% inf_add_revise_id] <- 
  paste0(data_2_index_vap$recordid[data_2_index_vap$recordid %in% inf_add_revise_id], "_VAP")

# Update record IDs for BSI episodes
data_2_index_bsi$recordid[data_2_index_bsi$recordid %in% inf_add_revise_id] <- 
  paste0(data_2_index_bsi$recordid[data_2_index_bsi$recordid %in% inf_add_revise_id], "_BSI")

# Combine the updated VAP and BSI data
data_2_index <- rbind(data_2_index_vap, data_2_index_bsi)

# Replace the filtered data in the original dataset
data[[2]][data[[2]]$redcap_repeat_instance == 1,] <- data_2_index

# -------------
# data[[5]] -> BSI
data_5_index_bsi <- data[[5]][which(data[[5]]$redcap_repeat_instance == 1),]
data_5_index_bsi$recordid[which(data_5_index_bsi$recordid %in% inf_add_revise_id)] <-
  paste0(data_5_index_bsi$recordid[which(data_5_index_bsi$recordid %in% inf_add_revise_id)], "_BSI")

data[[5]][which(data[[5]]$redcap_repeat_instance == 1),] <- data_5_index_bsi

# -------------
# data[[6]] -> VAP
data_6_index_vap <- data[[6]][which(data[[6]]$redcap_repeat_instance == 1),]
data_6_index_vap$recordid[which(data_6_index_vap$recordid %in% inf_add_revise_id)] <- 
  paste0(data_6_index_vap$recordid[which(data_6_index_vap$recordid %in% inf_add_revise_id)], "_VAP")

data[[6]][which(data[[6]]$redcap_repeat_instance == 1),] <- data_6_index_vap

# -------------
# Antibiotics
# Anti start and end date
anti_start <- data[[9]] %>% 
  select(starts_with("antib_start_date"))

anti_end <- data[[9]] %>% 
  select(starts_with("antib_end_date"))

anti_start_all <- do.call(pmax, c(anti_start, na.rm = TRUE))
anti_end_all <- do.call(pmax, c(anti_end, na.rm = TRUE))

# Antibiotics for specific episode
bsi_epi <- data[[9]] %>% 
  select(starts_with("bsi_antib"))

vap_epi <- data[[9]] %>% 
  select(starts_with("vap_antib"))

# Merge multiple columns into one column
bsi_epi_all <- do.call(pmax, c(bsi_epi, na.rm = TRUE))
vap_epi_all <- do.call(pmax, c(vap_epi, na.rm = TRUE))

# Combine
anti_treat <- data.frame(data[[9]]$recordid, 
                         anti_start_all, anti_end_all,
                         vap_epi_all, bsi_epi_all)

# Antibiotics names and group
# NA in anti names 
data[[9]]$antib[which(is.na(data[[9]]$antib))] <- 1000
#
anti_treat_add <- matrix(NA, nrow = nrow(data[[9]]), ncol = 2)
system.time({
  for (i in 1:nrow(data[[9]])) {
    for (j in 1:nrow(anti)) {
      if (data[[9]]$antib[i] == anti$antibiotics_f07e[j]) {
        anti_treat_add[i,1] <- anti$anti_names[j]
        anti_treat_add[i,2] <- anti$anti_group[j]
      } else {
        
      }
    }
  }
})

# Renames
anti_treat <- data.frame(anti_treat, anti_treat_add)
colnames(anti_treat) <- c("recordid", 
                          "anti_start", "anti_end",
                          "vap_epi", "bsi_epi",
                          "anti_names", 
                          "anti_group")

# Replace empty strings ("") with NA
anti_treat[anti_treat == ""] <- NA

# Identify and keep one row per set of duplicates within the same recordid
# And delete the all NA rows
deduplicated_rows_anti_treat <- anti_treat %>%
  group_by(recordid) %>%
  distinct() %>%
  ungroup() %>%
  filter(!(
    apply(select(., -recordid), 1, function(row) {
      all(str_trim(row) == "" | is.na(row))
    })
  ))

# Identify rows where `recordid` appears only once
single_occurrence_anti_treat <- anti_treat %>%
  group_by(recordid) %>%
  filter(n() == 1) %>%
  ungroup()

# Combine deduplicated rows, single occurrences, and filtered non-duplicate rows
anti_treat_clean <- bind_rows(deduplicated_rows_anti_treat, single_occurrence_anti_treat)

# Create VAP and BSI rows directly, with recordid suffix
anti_treat_revise_rows <- do.call(rbind, lapply(
  c("_VAP", "_BSI"),
  function(suffix) {
    rows <- anti_treat_clean[anti_treat_clean$recordid %in% inf_add_revise_id, ]
    rows$recordid <- paste0(rows$recordid, suffix)
    return(rows)
  }
))

# Remove original records and add revised rows
anti_treat_clean <- anti_treat_clean[!(anti_treat_clean$recordid %in% inf_add_revise_id), ]
anti_treat_index <- rbind.data.frame(anti_treat_clean, anti_treat_revise_rows)
```
## All recordid of those with VAP and BSI has been revised
# Baseline and outcomes
```{r}
# Date of enrollment and birth
birth_date <- c("dmdtc", "brthdtc")
birth_date_indices <- which(names(data[[1]]) %in% birth_date)
# as.Date
for (i in birth_date_indices) {data[[1]][,i] = as.Date(data[[1]][,i])}

# ------------------------------------------------------------
# Identify duplicate recordids
duplicate_recordid1 <- data[[1]]$recordid[duplicated(data[[1]]$recordid) | duplicated(data[[1]]$recordid, fromLast = TRUE)]

# Separate duplicate rows
duplicate_rows1 <- data[[1]][data[[1]]$recordid %in% duplicate_recordid1, ]

# Infection onset information for duplicate rows
duplicate_rows1_inf <- inf_add[inf_add$recordid %in% duplicate_rows1$recordid, ]

# Merge duplicate_rows1 and duplicate_rows1_inf based on recordid
data1_merged_data <- merge(duplicate_rows1, duplicate_rows1_inf, by = "recordid", suffixes = c("_data1", "_inf"))

# Calculate the absolute date difference
data1_merged_data$date_diff <- abs(as.Date(data1_merged_data$inf_onset) - as.Date(data1_merged_data$hpd_adm_date))

# Sort by recordid and date_diff
data1_merged_data <- data1_merged_data[order(data1_merged_data$recordid, data1_merged_data$date_diff), ]

# Filter the closest rows for duplicate recordid
data1_filtered_duplicate_rows <- data1_merged_data %>%
  group_by(recordid) %>%
  slice_min(order_by = date_diff, n = 1) %>%
  ungroup()

# Keep only the rows in data[[1]] that match the filtered duplicate rows
data1_filtered_rows <- data[[1]][data[[1]]$recordid %in% data1_filtered_duplicate_rows$recordid, ]

# Remove duplicate rows from data[[1]] and append the filtered rows
data1_non_duplicate_rows <- data[[1]][!data[[1]]$recordid %in% duplicate_recordid1, ]
data1_final_data <- bind_rows(data1_non_duplicate_rows, data1_filtered_rows)

# Ensure no duplicates remain
data1_final_data <- data1_final_data[!duplicated(data1_final_data$recordid), ]

# Update data[[1]] with the final result
data[[1]] <- data1_final_data

# -----------------------------------------
# Create baseline dataset
df_baseline <- matrix(NA, nrow = nrow(data[[1]]), ncol = 20)
colnames(df_baseline) <- c("recordid", "date_enrolment",
                           "age_raw", "age_new", "age_group", 
                           "age_display", "age_unit",
                           "country_ab", "country", 
                           "country_region", "country_income",
                           "sex", "hpd_adm_date", "hpd_hosp_date",
                           "hpd_admtype", "hpd_admreason", 
                           "comorbidities_CCI", "siteid", "cpis_score", 
                           "cmb_overnight_rhc_surgery")

# recordid
df_baseline[,"recordid"] <- data[[1]]$recordid

# Date of enrollment
df_baseline[,"date_enrolment"] <- as.character(data[[1]]$dmdtc)

# Age
# "age_raw"
system.time({
  for (i in 1:nrow(data[[1]])) {
    if (!is.na(data[[1]]$brthdtc[i])) {
      df_baseline[i,"age_raw"] <- interval(data[[1]]$brthdtc[i], data[[1]]$dmdtc[i])/years(1)
    } else {
      data[[1]]$agey[which(is.na(data[[1]]$agey))] <- 0
      data[[1]]$agem[which(is.na(data[[1]]$agem))] <- 0
      data[[1]]$aged[which(is.na(data[[1]]$aged))] <- 0
      df_baseline[i,"age_raw"] <- data[[1]]$agey[i]+data[[1]]$agem[i]/12+data[[1]]$aged[i]/365
    } 
  }
})
# Trans "age_raw" to numeric
numeric_vector <- vector()

for (char in df_baseline[,"age_raw"]) {
  num <- as.numeric(gsub('"', '', char))
  numeric_vector <- c(numeric_vector, num)
}

# "age_new"
system.time({
  df_baseline[,"age_new"] <- ifelse(numeric_vector >= 1, floor(numeric_vector), 
                             ifelse(numeric_vector > 0, round(numeric_vector, 3), NA))
})

# "age_group" (Adults, Child and Neonatal)
system.time({
  df_baseline[,"age_group"] <- ifelse(numeric_vector >= 18, 1,
                                      ifelse(numeric_vector > 28/365 & numeric_vector < 18, 2,
                                             ifelse(numeric_vector > 0 & numeric_vector <= 28/365, 3, NA)))
})


# Age display (for neonatal days)
for (i in 1:nrow(data[[1]])) {
  grp <- df_baseline[i, "age_group"]
  
  if (!is.na(grp)) {
    if (grp %in% c(1, 2)) {
      # Adults & children: use age_new (years)
      df_baseline[i, "age_display"] <- df_baseline[i, "age_new"]
      df_baseline[i, "age_unit"]    <- "years"
      
    } else if (grp == 3) {
      # Neonates: exact days
      if (!is.na(data[[1]]$brthdtc[i]) && !is.na(data[[1]]$dmdtc[i])) {
        df_baseline[i, "age_display"] <- as.numeric(interval(data[[1]]$brthdtc[i],
                                                             data[[1]]$dmdtc[i]) / days(1))
      } else {
        df_baseline[i, "age_display"] <- data[[1]]$aged[i]
      }
      df_baseline[i, "age_unit"] <- "days"
    }
  }
}

# --------
# Revise error site id
data[[1]]$f07m_siteid_1[which(data[[1]]$f07m_siteid_1 == "PH003")] <- "PK003"
# --------
# "country_ab" 
df_baseline[,"country_ab"] <- substr(data[[1]]$f07m_siteid_1, 1, 2)
# Revise country_ab of Mongolia and Sri Lanka
df_baseline[,"country_ab"] <- ifelse(df_baseline[,"country_ab"] == "MG", "MN",
                                     ifelse(df_baseline[,"country_ab"] == "SL", "LK",
                                            df_baseline[,"country_ab"]))

# Trans to country names
df_baseline[,"country"] <- countrycode(df_baseline[,"country_ab"], 
                                       origin = 'iso2c',  
                                       destination = 'cldr.name.en')

# Add country region based on WHO
country_to_region <- list(
  "South-East Asian Region" = c("Indonesia", "Thailand", "Timor-Leste",
                                "Bangladesh", "Nepal", "Sri Lanka", "India"),
  
  "Western Pacific Region" = c("Singapore", "Brunei", "Cambodia",
                               "Malaysia","Philippines", "Vietnam", 
                               "Hong Kong SAR China", "Japan", 
                               "Mongolia", "Taiwan", "China"),
  
  "Eastern Mediterranean Region" = c("Pakistan")
)

#
df_baseline[,"country_region"] <- sapply(df_baseline[,"country"], function(country) {
  for (region in names(country_to_region)) {
    if (country %in% country_to_region[[region]]) {
      return(region)
    }
  }
  return(NA)  
})

# World bank income status
country_to_income <- list(
  "High income" = c("Singapore", "Brunei", "Hong Kong SAR China", "Japan", "Taiwan"),
  "Upper middle income" = c("Mongolia", "Malaysia", "Thailand", "China", "Indonesia"),
  "Lower middle income" = c("Bangladesh", "Nepal", "Cambodia", 
                            "Philippines", "Pakistan", "Sri Lanka", 
                            "Timor-Leste", "Vietnam", "India")
)

# 
df_baseline[,"country_income"] <- sapply(df_baseline[,"country"], function(country) {
  for (income in names(country_to_income)) {
    if (country %in% country_to_income[[income]]) {
      return(income)
    }
  }
  return(NA)  
})

# Sex
df_baseline[,"sex"] <- data[[1]]$sex

# Date of admission
df_hpd_adm_date <- as.Date(data[[1]]$hpd_adm_date, format="%Y-%m-%d")
df_baseline[,"hpd_adm_date"] <- as.character(df_hpd_adm_date)

# Date of hospitalisation (if transfer from another facility)
df_hpd_hosp_date <- as.Date(data[[1]]$hpd_hosp_date, format="%Y-%m-%d")
df_baseline[,"hpd_hosp_date"] <- as.character(df_hpd_hosp_date)

# Admission type 
df_baseline[,"hpd_admtype"] <- data[[1]]$hpd_admtype

# Primary admission reason
df_baseline[,"hpd_admreason"] <- data[[1]]$hpd_admreason

# Comorbidities (Charlson score)
cmb_comorbidities <- data[[1]] %>%
  select(starts_with("cmb_comorbidities"))

system.time({
  for (i in 1:nrow(data[[1]])) {
    if (data[[1]]$cmb_comorbidities___none[i] == 1) {
      
      df_baseline[i,"comorbidities_CCI"] <- 0
      
    } else if (data[[1]]$cmb_comorbidities___none[i] == 0) {
      
      df_baseline[i,"comorbidities_CCI"] <- 
        2*data[[1]]$cmb_comorbidities___cog[i] + 
        2*data[[1]]$cmb_comorbidities___dem[i] +
        data[[1]]$cmb_comorbidities___cpd[i] + 
        data[[1]]$cmb_comorbidities___rheu[i] + 
        0*data[[1]]$cmb_comorbidities___pep[i] +
        2*data[[1]]$cmb_comorbidities___mld[i] +
        0*data[[1]]$cmb_comorbidities___diab[i] +
        data[[1]]$cmb_comorbidities___diad[i] +
        2*data[[1]]$cmb_comorbidities___hop[i] +
        data[[1]]$cmb_comorbidities___renal[i] + 
        2*data[[1]]$cmb_comorbidities___onc[i] +
        4*data[[1]]$cmb_comorbidities___liv[i] +
        6*data[[1]]$cmb_comorbidities___mst[i] +
        4*data[[1]]$cmb_comorbidities___aids[i]+
        0*data[[1]]$cmb_comorbidities___oth[i]
      
    } else {
      
    }
  }
})

# Siteid
df_baseline[,"siteid"] <- data[[1]]$f07m_siteid_1

## Trans to data.frame
df_baseline <- cbind.data.frame(df_baseline, cmb_comorbidities)

# Add infection types and onset date to baseline ("infection_types", "inf_onset")
df_baseline <- left_join(df_baseline, inf_add, by = "recordid")

# Check for healthcare-associated BSI
df_baseline[,"cmb_overnight_rhc_surgery"] <- apply(data[[1]][, c("cmb_overnight", "cmb_rhc", "cmb_surgery")],
  1,
  function(x) {
    if ("Y" %in% x) {
      return("Y")
    } else if ("N" %in% x) {
      return("N")
    } else if ("UNK" %in% x) {
      return("UNK")
    } else {
      return(NA)
    }
  }
)

#####
# SOFA (F07a, F07b)
# Function for sum up with NA
rowSumsWithNA <- function(x) {
  apply(x, 1, function(row) if (any(is.na(row))) NA else sum(row, na.rm = TRUE))
}
###
# Index sofa raw data
sofa_bsi <- data[[5]][which(data[[5]]$redcap_repeat_instance == 1),] %>% 
  select("recordid", starts_with("sofa_"))
sofa_vap <- data[[6]][which(data[[6]]$redcap_repeat_instance == 1),] %>% 
  select("recordid", starts_with("sofa_")) 
# Retain index rows based on infection types
sofa_vap_id <- inf_add %>%
  filter(infection_types == "VAP") %>%
  pull(recordid)

sofa_bsi_id <- inf_add %>%
  filter(infection_types %in% c("Hospital-acquired BSI", "Healthcare-associated BSI")) %>%
  pull(recordid)
#
sofa_bsi <- sofa_bsi[sofa_bsi$recordid %in% sofa_bsi_id,]
sofa_vap <- sofa_vap[sofa_vap$recordid %in% sofa_vap_id,]
# Standardize column names
colnames(sofa_bsi) <- gsub("_bsi", "", colnames(sofa_bsi))
colnames(sofa_vap) <- gsub("_vap", "", colnames(sofa_vap))
# Combine the data frames
sofa_all <- rbind(sofa_bsi, sofa_vap)
#
sofa_new <- matrix(NA, nrow = nrow(sofa_all), ncol = 8)
colnames(sofa_new) <- c("recordid", "score_respiration", 
                        "score_coagulation", "score_liver",
                        "score_CVS", "score_CNV",
                        "score_renal", "sofa_score")

## recordid
sofa_new[,"recordid"] <- sofa_all$recordid

## respiration
# Combine 
sofa_all$sofa_score_1_1 <- ifelse(is.na(sofa_all$sofa_score_1_1), sofa_all$sofa_score_1_1_2, sofa_all$sofa_score_1_1)
#
sofa_new[,"score_respiration"] <- as.numeric(sofa_all$sofa_score_1_1)

## coagulation
sofa_new[,"score_coagulation"] <- as.numeric(ifelse(is.na(sofa_all$sofa_score_2_1), 0, sofa_all$sofa_score_2_1))

## liver
# Combine
sofa_all$sofa_score_3_1 <- ifelse(is.na(sofa_all$sofa_score_3_1), sofa_all$sofa_score_3_1_2, sofa_all$sofa_score_3_1)

sofa_all$sofa_score_3_1_3 <- ifelse(is.na(sofa_all$sofa_score_3_1_3), sofa_all$sofa_score_3_1, sofa_all$sofa_score_3_1_3)
#
sofa_new[,"score_liver"] <- as.numeric(sofa_all$sofa_score_3_1_3)

## CVS
system.time({
  
  # MAP<70 mmHg 
  condition2 <- !is.na(sofa_all$sofa_map) & sofa_all$sofa_map < 70
  sofa_new[condition2, "score_CVS"] <- 1
  
  # Dopamine <5 or dobutamine (any dose)
  condition3 <- (sofa_all$sofa_car_dop_1 <= 5) | (sofa_all$sofa_car_dob == 1)
  sofa_new[condition3, "score_CVS"] <- 2
  
  # Dopamine >5 or epinephrine <0.1 or norepinephrine <0.1 
  condition4 <- ((sofa_all$sofa_car_dop_1 > 5) & (sofa_all$sofa_car_dop_1 <= 15)) | (sofa_all$sofa_car_epi_1 <= 0.1) | (sofa_all$sofa_car_nor_1 <= 0.1)
  sofa_new[condition4, "score_CVS"] <- 3
  
  # Dopamine >15 or epinephrine >0.1 or norepinephrine >0.1 
  condition5 <- (sofa_all$sofa_car_dop_1 > 15) | (sofa_all$sofa_car_epi_1 > 0.1) | (sofa_all$sofa_car_nor_1 > 0.1)
  sofa_new[condition5, "score_CVS"] <- 4

  # sofa_map >= 70 or no use (dopamine, dobutamine, epinephrine, norepinephrine)
  condition1 <- (!is.na(sofa_all$sofa_map) & sofa_all$sofa_map >= 70) | (sofa_all$sofa_car_dop == 0)| (sofa_all$sofa_car_dob == 0) | (sofa_all$sofa_car_nor == 0)
  sofa_new[condition1, "score_CVS"] <- 0
  
})

## CNV
# Sum up
sofa_all$sofa_cen_total <- rowSumsWithNA(cbind(sofa_all$sofa_cen_1, sofa_all$sofa_cen_2, sofa_all$sofa_cen_3))
# Set different scores for CNV
system.time({
  for (i in 1:nrow(sofa_all)) {
    if (is.na(sofa_all$sofa_cen_total[i])) {
      # For NA
      sofa_new[i, "score_CNV"] <- 0
    } else if (sofa_all$sofa_cen_total[i] > 14) {
      sofa_new[i, "score_CNV"] <- 0
    } else if ((sofa_all$sofa_cen_total[i] == 14) | (sofa_all$sofa_cen_total[i] == 13)) {
      sofa_new[i, "score_CNV"] <- 1
    } else if ((sofa_all$sofa_cen_total[i] <= 12) & (sofa_all$sofa_cen_total[i] >= 10)) {
      sofa_new[i, "score_CNV"] <- 2
    } else if ((sofa_all$sofa_cen_total[i] <= 9) & (sofa_all$sofa_cen_total[i] >= 6)) {
      sofa_new[i, "score_CNV"] <- 3
    } else if (sofa_all$sofa_cen_total[i] <= 5) {
      sofa_new[i, "score_CNV"] <- 4
    }
  }
})

## renal
# Combine
sofa_all$sofa_score_6_1 <- ifelse(is.na(sofa_all$sofa_score_6_1), sofa_all$sofa_score_6_1_2, sofa_all$sofa_score_6_1)
#
sofa_new[, "score_renal"] <- as.numeric(as.character(sofa_all$sofa_score_6_1))

sofa_new[, "score_renal"][is.na(sofa_new[, "score_renal"])] <- 0

## Total SOFA scores
sofa_new <- as.data.frame(sofa_new)

sofa_items <- c("score_respiration", "score_coagulation", "score_liver",
                "score_CVS", "score_CNV", "score_renal")
sofa_items_indices <- which(names(sofa_new) %in% sofa_items)

for (i in sofa_items_indices) {sofa_new[, i] = as.numeric(as.character(sofa_new[, i]))}
#
sofa_new[,"sofa_score"] <- rowSumsWithNA(sofa_new[, sofa_items_indices])

#####
## Severity score and admission ward types
# Clinical severity signs (qSOFA for adults, sepsis six recognition features for children, general WHO severity signs for neonates)
# Retain index rows based on organism types
severity_used <- data[[2]][which(data[[2]]$redcap_repeat_instance == 1),]

df_severity_bsi <- severity_used[which(severity_used$redcap_event_name %in% "bsi_episode_arm_1"),]
df_severity_vap <- severity_used[which(severity_used$redcap_event_name %in% "vap_episode_arm_1"),]

severity_bsi <- df_severity_bsi[df_severity_bsi$recordid %in% sofa_bsi_id,]
severity_vap <- df_severity_vap[df_severity_vap$recordid %in% sofa_vap_id,]

severity <- rbind(severity_vap, severity_bsi)

# Add age group (severity calculation varies across different age groups)
severity <- left_join(severity, df_baseline[,c("recordid", "age_group")], by = "recordid")
# 
severity_new <- matrix(NA, nrow = nrow(severity), ncol = 5)
colnames(severity_new) <- c("recordid", "adm_ward_types_ori", "adm_ward_types_new",
                            "severity_score", "severity_score_scale")
#
severity_new[,"recordid"] <- severity$recordid
# Admission ward types
severity_new[, "adm_ward_types_ori"] <- severity$hpd_adm_wardtype

# ICU OR non-ICU
severity_new[, "adm_ward_types_new"] <- ifelse(
  grepl("ICU", severity$hpd_adm_wardtype), 
  "ICU", 
  ifelse(
    is.na(severity$hpd_adm_wardtype), 
    NA, 
    "General ward"
  )
)

# Conversion function ("Y" to 1, "N" or "UNK" to 0)
convert_to_binary <- function(value) {
  if (is.na(value) || value == "") {
    return(NA)
  } else if (value == "Y") {
    return(1)
  } else {
    return(0)
  }
}

# List of columns to convert from severity
columns_severity <- c("ser_gcs_under15", "ser_rr_22up", "ser_sbp_under100", 
                      "ser_abnormal_temp", "ser_inapp_tachycardia", 
                      "ser_alter_mental", "ser_reduce_pp",
                      "ser_neo_reduce", "ser_neo_feed", "ser_neo_convul")

# Apply the conversion function to each column in severity
for (column in columns_severity) {
  new_column <- paste0(column, "_new")
  severity[[new_column]] <- unlist(lapply(severity[[column]], convert_to_binary))
}

# Define age groups, ensuring no NAs
age_adult <- !is.na(severity$age_group) & severity$age_group == 1
age_child <- !is.na(severity$age_group) & severity$age_group == 2
age_neo <- !is.na(severity$age_group) & severity$age_group == 3

# Apply row sums to the appropriate rows based on age groups
severity_new[age_adult, "severity_score"] <- rowSumsWithNA(severity[age_adult, c("ser_gcs_under15_new", "ser_rr_22up_new", "ser_sbp_under100_new")])

severity_new[age_child, "severity_score"] <- rowSumsWithNA(severity[age_child, c("ser_abnormal_temp_new", "ser_inapp_tachycardia_new", "ser_alter_mental_new", "ser_reduce_pp_new")])

severity_new[age_neo, "severity_score"] <- rowSumsWithNA(severity[age_neo, c("ser_neo_reduce_new", "ser_neo_feed_new", "ser_neo_convul_new")])

# Trans chr to num
severity_new <- as.data.frame(severity_new)
severity_new[, "severity_score"] <- as.numeric(severity_new[, "severity_score"])

# scale severity scores
scale_severity <- function(data, age_group) {
  if (any(!is.na(data[age_group, "severity_score"]))) {
    max_score <- max(data[age_group, "severity_score"], na.rm = TRUE)
    data[age_group, "severity_score_scale"] <- ifelse(is.na(data[age_group, "severity_score"]), 
                                                   NA, 
                                                   12 * data[age_group, "severity_score"] / max_score)
  }
  return(data)
}

# Apply function to each age group
severity_new <- scale_severity(severity_new, age_adult)
severity_new <- scale_severity(severity_new, age_child)
severity_new <- scale_severity(severity_new, age_neo)

#####
## CPIS score for VAP (F07b, F02)
## Age categories (years old): (1) > 12, (2) <= 1, (3) > 1 to <= 12
# Index data
cpis_used <- data[[6]][which(data[[6]]$redcap_repeat_instance == 1),]
cpis_raw <- cpis_used[cpis_used$recordid %in% sofa_vap_id,]

cpis_add_temp <- severity[, c("recordid", "ser_abnormal_temp_adult", "ser_abnormal_temp")]
cpis_add_ps <- sofa_vap[, c("recordid", "sofa_res_3")]

cpis_add_list <- list(cpis_raw, cpis_add_temp, cpis_add_ps)
cpis_raw <- reduce(cpis_add_list, left_join, by = "recordid")

###
cpis_new <- matrix(NA, nrow = nrow(cpis_raw), ncol = 8)
colnames(cpis_new) <- c("recordid", 
                        "temperature", "wbc", "tracheal_secretion", 
                        "pa_fi", "pulmonary_radiography", "culture_ta",
                        "cpis_score")

# recordid
cpis_new[,"recordid"] <- cpis_raw$recordid

# Trans to 1,0
columns_cpis <- c("temp_cxr", "ser_abnormal_temp_adult", 
                  "temp_ins", "fev_hyp", "ser_abnormal_temp",
                  "white_bc", "leu", "leu_1",
                  "new_onset_ps", "new_onset_ps_1",
                  "wor_ge", "wor_ge_1", "wor_ge_2",
                  "cxr_1")

# Apply the conversion function to each column in severity
for (column in columns_cpis) {
  new_column <- paste0(column, "_new")
  cpis_raw[[new_column]] <- unlist(lapply(cpis_raw[[column]], convert_to_binary))
}

# temperature
# Define a helper function to create temp groups
create_temp_group <- function(data, col1, col2) {
  ifelse(
    data[[col1]] == 1 | data[[col2]] == 1, 
    1,
    ifelse(
      (data[[col1]] == 0 | data[[col2]] == 0) & 
      !(data[[col1]] == 1 | data[[col2]] == 1), 
      0, 
      NA
    )
  )
}

# Apply the helper function to create temp groups
cpis_raw$temp_group_1 <- create_temp_group(cpis_raw, "ser_abnormal_temp_adult_new", "temp_cxr_new")
cpis_raw$temp_group_2 <- create_temp_group(cpis_raw, "ser_abnormal_temp_new", "temp_ins_new")
cpis_raw$temp_group_3 <- create_temp_group(cpis_raw, "ser_abnormal_temp_new", "fev_hyp_new")

# Use coalesce to combine temp groups
cpis_new[,"temperature"] <- coalesce(cpis_raw$temp_group_1, cpis_raw$temp_group_2, cpis_raw$temp_group_3)

# WBC
cpis_new[,"wbc"] <- coalesce(cpis_raw$white_bc_new, cpis_raw$leu_new, cpis_raw$leu_1_new)

# tracheal_secretion
cpis_new[,"tracheal_secretion"] <- coalesce(cpis_raw$new_onset_ps_new, cpis_raw$new_onset_ps_1_new)

# PaO2/FiO2
 cpis_raw$wor_ge_group_1 <-  ifelse(
  cpis_raw$sofa_res_3 <= 240 | cpis_raw$wor_ge_new == 1, 
  1,
  ifelse(
    (cpis_raw$sofa_res_3 > 240 | cpis_raw$wor_ge_new == 0) & 
    !(cpis_raw$sofa_res_3 <= 240 | cpis_raw$wor_ge_new == 1), 
    0, 
    NA
  )
)

cpis_new[,"pa_fi"] <- coalesce(cpis_raw$wor_ge_group_1, cpis_raw$wor_ge_1_new, cpis_raw$wor_ge_2_new)

# Pulmonary radiography
cpis_new[,"pulmonary_radiography"] <- cpis_raw$cxr_1_new

# Set 0 in the new onset of purulent sputum or change in character of sputum (second group)
cpis_new_na.ps <- which(is.na(cpis_new[, "tracheal_secretion"])) # 0
cpis_new[cpis_new_na.ps, "tracheal_secretion"] <- 0

#####
## PITT for BSI (F07a)
# Calculation on PITT itemwise score
# Index
pitt_used <- data[[5]][which(data[[5]]$redcap_repeat_instance == 1),]

pitt_raw <- pitt_used[pitt_used$recordid %in% sofa_bsi_id,]
#
pitt_new <- matrix(NA, nrow = nrow(pitt_raw), ncol = 14)
colnames(pitt_new) <- c("recordid", 
                        "temp", "hypotension", "mv", 
                        "cardiac", "mental", "pitt_score",
                        "res_qpitt", "sys_qpitt", "mental_qpitt",
                        "temp_qpitt", "ca_qpitt", "qpitt_score", "UTI_source")

# recordid
pitt_new[,"recordid"] <- pitt_raw$recordid

# source
pitt_new[,"UTI_source"] <- pitt_raw$bsi_pri_sec_1___4

# Temperature
system.time({
  pitt_new[,"temp"] <- ifelse(
    !is.na(pitt_raw$temp_1) & pitt_raw$temp_1 >= 36.1 & pitt_raw$temp_1 <= 38.9, 0,
    ifelse(
      !is.na(pitt_raw$temp_1) & ((pitt_raw$temp_1 >= 35.1 & pitt_raw$temp_1 <= 36) | (pitt_raw$temp_1 >= 39 & pitt_raw$temp_1 <= 39.9)), 1,
      ifelse(!is.na(pitt_raw$temp_1) & (pitt_raw$temp_1 <= 35 | pitt_raw$temp_1 >= 40), 2, NA)
    )
  )
})

# "hypotension" (acute hypotensive event, IV agents required, SBP<90 mmHg)
condition_hyp <- (pitt_raw$acute == 1) | (pitt_raw$iv_agents == 1) | (pitt_raw$sys_bp_1 < 90)
condition_hyp_other <- (pitt_raw$acute %in% c(2,3)) | (pitt_raw$iv_agents %in% c(2,3)) | (pitt_raw$sys_bp == 2) | (pitt_raw$sys_bp_1 >= 90)

pitt_new[condition_hyp, "hypotension"] <- 2
pitt_new[condition_hyp_other, "hypotension"] <- 0

# mechanical ventilation
condition_mv <- pitt_raw$mv == 1
condition_mv_other <- pitt_raw$mv %in% c(2,3)

pitt_new[condition_mv, "mv"] <- 2
pitt_new[condition_mv_other, "mv"] <- 0

# cardiac arrest
condition_ca <- pitt_raw$ca == 1
condition_ca_other <- pitt_raw$ca %in% c(2,3)

pitt_new[condition_ca, "cardiac"] <- 4
pitt_new[condition_ca_other, "cardiac"] <- 0

# mental
pitt_new[, "mental"] <- ifelse(pitt_raw$men_sta %in% c(1,5), 0,
                               ifelse(pitt_raw$men_sta == 2, 1,
                                      ifelse(pitt_raw$men_sta == 3, 2,
                                             ifelse(pitt_raw$men_sta == 4, 4, NA))))

#####
## qPITT for BSI
# "res_qpitt"
condition_res_qpitt <- (pitt_raw$res_rate_1 >= 25) | (pitt_raw$mv == 1)
condition_res_qpitt_other <-  (pitt_raw$res_rate == 2) | (pitt_raw$res_rate_1 < 25) | (pitt_raw$mv %in% c(2,3))

pitt_new[condition_res_qpitt, "res_qpitt"] <- 1
pitt_new[condition_res_qpitt_other, "res_qpitt"] <- 0

# "sys_qpitt"
condition_sys_qpitt <- pitt_raw$sys_bp_1 <= 90
condition_sys_qpitt_other <- (pitt_raw$sys_bp == 2) | (pitt_raw$sys_bp_1 > 90)

pitt_new[condition_sys_qpitt, "sys_qpitt"] <- 1
pitt_new[condition_sys_qpitt_other, "sys_qpitt"] <- 0

# "mental_qpitt"
condition_mental_qpitt <- pitt_raw$men_sta == 1
condition_mental_qpitt_other <- pitt_raw$men_sta %in% c(2:5)

pitt_new[condition_mental_qpitt, "mental_qpitt"] <- 1
pitt_new[condition_mental_qpitt_other, "mental_qpitt"] <- 0

# "temp_qpitt
condition_temp_qpitt <- pitt_raw$temp_1 < 36
condition_temp_qpitt_other <- (pitt_raw$temp == 2) | (pitt_raw$temp_1 >= 36)

pitt_new[condition_temp_qpitt, "temp_qpitt"] <- 1
pitt_new[condition_temp_qpitt_other, "temp_qpitt"] <- 0

# "ca_qpitt"
condition_ca_qpitt <- pitt_raw$ca == 1
condition_ca_qpitt_other <- pitt_raw$ca %in% c(2,3)

pitt_new[condition_ca_qpitt, "ca_qpitt"] <- 1
pitt_new[condition_ca_qpitt_other, "ca_qpitt"] <- 0
#
pitt_new <- as.data.frame(pitt_new)

###
# Sum up of PITT and qPITT
pitt_col <- c("temp", "hypotension", "mv", "cardiac", "mental")
qpitt_col <- c("res_qpitt", "sys_qpitt", "mental_qpitt", "temp_qpitt", "ca_qpitt")
#
pitt_col_indices <- which(names(pitt_new) %in% pitt_col)
qpitt_col_indices <- which(names(pitt_new) %in% qpitt_col)
col_indices <- c(pitt_col_indices, qpitt_col_indices)

for (i in col_indices) {pitt_new[, i] = as.numeric(as.character(pitt_new[, i]))}
pitt_new[, "pitt_score"] <- rowSumsWithNA(pitt_new[, pitt_col_indices])
pitt_new[, "qpitt_score"] <- rowSumsWithNA(pitt_new[, qpitt_col_indices])

#####
## EQ-5D-3L for subject alive prior to day 28 from last infection
## subject more than 12 years old (func_status_fo == 1 & sub_died_pri_day28 == 2)
## FBIS scores (func_status_fo == 1)

# All five EQ-5D-3L dimensions are level 1 (with no NA)
is_11111 <- function(df) {
  vals <- cbind(df$eq_fo, df$eq_fo_1, df$eq_fo_2, df$eq_fo_3, df$eq_fo_4)
  rowSums(vals == 1) == 5 & rowSums(is.na(vals)) == 0
}

# Data join
eq_raw <- dplyr::left_join(
  data[[8]],
  df_baseline[, c("recordid", "country")],
  by = "recordid"
)

eq_new <- matrix(
  NA_real_,
  nrow = nrow(eq_raw),
  ncol = 9,
  dimnames = list(
    NULL,
    c("recordid", "sub_died_pri_day28",
      "eq_5d_3l_1", "eq_5d_3l_2", "eq_5d_3l_3", "eq_5d_3l_4", "eq_5d_3l_5",
      "eq_5d_3l", "fbis_score")
  )
)

# Copy over identifiers and raw levels
eq_new[, "recordid"] <- eq_raw$recordid
eq_new[, "sub_died_pri_day28"] <- eq_raw$sub_died_pri_day28
eq_new[, "eq_5d_3l_1"] <- eq_raw$eq_fo
eq_new[, "eq_5d_3l_2"] <- eq_raw$eq_fo_1
eq_new[, "eq_5d_3l_3"] <- eq_raw$eq_fo_2
eq_new[, "eq_5d_3l_4"] <- eq_raw$eq_fo_3
eq_new[, "eq_5d_3l_5"] <- eq_raw$eq_fo_4

# Subject is alive prior to day 28 AND func_status_fo == 1
eq_condition <- (eq_raw$sub_died_pri_day28 == 2) & (eq_raw$func_status_fo == 1)

# ----------------------------
# Singapore (incl. Brunei, Hong Kong SAR China)
# ----------------------------
SG_ori <- eq_raw$country %in% c("Singapore", "Brunei", "Hong Kong SAR China")
SG <- SG_ori & !is.na(eq_condition) & eq_condition
SG_idx <- which(SG)

disut_mo_sg <- ifelse(SG & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.1678,
                                    ifelse(eq_raw$eq_fo==3, 0.3040, NA_real_))),
                      NA_real_)
disut_sc_sg <- ifelse(SG & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.1615,
                                    ifelse(eq_raw$eq_fo_1==3, 0.3465, NA_real_))),
                      NA_real_)
disut_ua_sg <- ifelse(SG & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.2555,
                                    ifelse(eq_raw$eq_fo_2==3, 0.3209, NA_real_))),
                      NA_real_)
disut_pd_sg <- ifelse(SG & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.1462,
                                    ifelse(eq_raw$eq_fo_3==3, 0.2291, NA_real_))),
                      NA_real_)
disut_ad_sg <- ifelse(SG & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.1501,
                                    ifelse(eq_raw$eq_fo_4==3, 0.2784, NA_real_))),
                      NA_real_)

n3_sg <- ifelse(
  SG,
  as.numeric(rowSums(cbind(eq_raw$eq_fo==3,
                           eq_raw$eq_fo_1==3,
                           eq_raw$eq_fo_2==3,
                           eq_raw$eq_fo_3==3,
                           eq_raw$eq_fo_4==3), na.rm = TRUE) > 0) * 0.2905,
  NA_real_
)

eq_index_sg <- 1 - (disut_mo_sg + disut_sc_sg + disut_ua_sg + disut_pd_sg + disut_ad_sg + n3_sg)
eq_index_sg[SG & is_11111(eq_raw)] <- 1
eq_new[SG_idx, "eq_5d_3l"] <- round(eq_index_sg[SG_idx], 3)

# ----------------------------
# Japan
# ----------------------------
JP_ori <- eq_raw$country == "Japan"
JP <- JP_ori & !is.na(eq_condition) & eq_condition
JP_idx <- which(JP)

disut_mo_jp <- ifelse(JP & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.075,
                                    ifelse(eq_raw$eq_fo==3, 0.418, NA_real_))),
                      NA_real_)
disut_sc_jp <- ifelse(JP & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.054,
                                    ifelse(eq_raw$eq_fo_1==3, 0.102, NA_real_))),
                      NA_real_)
disut_ua_jp <- ifelse(JP & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.044,
                                    ifelse(eq_raw$eq_fo_2==3, 0.133, NA_real_))),
                      NA_real_)
disut_pd_jp <- ifelse(JP & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.080,
                                    ifelse(eq_raw$eq_fo_3==3, 0.194, NA_real_))),
                      NA_real_)
disut_ad_jp <- ifelse(JP & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.063,
                                    ifelse(eq_raw$eq_fo_4==3, 0.112, NA_real_))),
                      NA_real_)

eq_index_jp <- 1 - 0.152 - (disut_mo_jp + disut_sc_jp + disut_ua_jp + disut_pd_jp + disut_ad_jp)
eq_index_jp[JP & is_11111(eq_raw)] <- 1
eq_new[JP_idx, "eq_5d_3l"] <- round(eq_index_jp[JP_idx], 3)

# ----------------------------
# Taiwan
# ----------------------------
TW_ori <- eq_raw$country == "Taiwan"
TW <- TW_ori & !is.na(eq_condition) & eq_condition
TW_idx <- which(TW)

disut_mo_tw <- ifelse(TW & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.123,
                                    ifelse(eq_raw$eq_fo==3, 0.272, NA_real_))),
                      NA_real_)
disut_sc_tw <- ifelse(TW & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.167,
                                    ifelse(eq_raw$eq_fo_1==3, 0.276, NA_real_))),
                      NA_real_)
disut_ua_tw <- ifelse(TW & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.085,
                                    ifelse(eq_raw$eq_fo_2==3, 0.208, NA_real_))),
                      NA_real_)
disut_pd_tw <- ifelse(TW & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.121,
                                    ifelse(eq_raw$eq_fo_3==3, 0.261, NA_real_))),
                      NA_real_)
disut_ad_tw <- ifelse(TW & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.154,
                                    ifelse(eq_raw$eq_fo_4==3, 0.282, NA_real_))),
                      NA_real_)

n3_tw <- ifelse(
  TW,
  as.numeric(rowSums(cbind(eq_raw$eq_fo==3,
                           eq_raw$eq_fo_1==3,
                           eq_raw$eq_fo_2==3,
                           eq_raw$eq_fo_3==3,
                           eq_raw$eq_fo_4==3), na.rm = TRUE) > 0) * 0.19,
  NA_real_
)

eq_index_tw <- 1 - 0.185 - (disut_mo_tw + disut_sc_tw + disut_ua_tw + disut_pd_tw + disut_ad_tw + n3_tw)
eq_index_tw[TW & is_11111(eq_raw)] <- 1
eq_new[TW_idx, "eq_5d_3l"] <- round(eq_index_tw[TW_idx], 3)

# ----------------------------
# China
# ----------------------------
CN_ori <- eq_raw$country == "China"
CN <- CN_ori & !is.na(eq_condition) & eq_condition
CN_idx <- which(CN)

disut_mo_cn <- ifelse(CN & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.0766,
                                    ifelse(eq_raw$eq_fo==3, 0.2668, NA_real_))),
                      NA_real_)
disut_sc_cn <- ifelse(CN & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.0441,
                                    ifelse(eq_raw$eq_fo_1==3, 0.2912, NA_real_))),
                      NA_real_)
disut_ua_cn <- ifelse(CN & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.0370,
                                    ifelse(eq_raw$eq_fo_2==3, 0.0538, NA_real_))),
                      NA_real_)
disut_pd_cn <- ifelse(CN & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.0274,
                                    ifelse(eq_raw$eq_fo_3==3, 0.0409, NA_real_))),
                      NA_real_)
disut_ad_cn <- ifelse(CN & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.0359,
                                    ifelse(eq_raw$eq_fo_4==3, 0.1771, NA_real_))),
                      NA_real_)

eq_index_cn <- 1 - (disut_mo_cn + disut_sc_cn + disut_ua_cn + disut_pd_cn + disut_ad_cn)
eq_new[CN_idx, "eq_5d_3l"] <- round(eq_index_cn[CN_idx], 3)

# ----------------------------
# Thailand (incl. Mongolia, Indonesia)
# ----------------------------
TH_ori <- eq_raw$country %in% c("Thailand", "Mongolia", "Indonesia")
TH <- TH_ori & !is.na(eq_condition) & eq_condition
TH_idx <- which(TH)

mo <- ifelse(TH & eq_raw$eq_fo   == 2, 1, ifelse(TH & eq_raw$eq_fo   == 3, 2, 0))
sc <- ifelse(TH & eq_raw$eq_fo_1 == 2, 1, ifelse(TH & eq_raw$eq_fo_1 == 3, 2, 0))
ua <- ifelse(TH & eq_raw$eq_fo_2 == 2, 1, ifelse(TH & eq_raw$eq_fo_2 == 3, 2, 0))
pd <- ifelse(TH & eq_raw$eq_fo_3 == 2, 1, ifelse(TH & eq_raw$eq_fo_3 == 3, 2, 0))
ad <- ifelse(TH & eq_raw$eq_fo_4 == 2, 1, ifelse(TH & eq_raw$eq_fo_4 == 3, 2, 0))

m2 <- ifelse(TH & eq_raw$eq_fo   == 3, 1, 0)
p2 <- ifelse(TH & eq_raw$eq_fo_3 == 3, 1, 0)
a2 <- ifelse(TH & eq_raw$eq_fo_4 == 3, 1, 0)

n3 <- ifelse(
  TH & (eq_raw$eq_fo==3 | eq_raw$eq_fo_1==3 | eq_raw$eq_fo_2==3 |
        eq_raw$eq_fo_3==3 | eq_raw$eq_fo_4==3),
  1, 0
)

eq_index_th <- 1 - 0.202 -
  (0.121 * mo) - (0.121 * sc) - (0.059 * ua) - (0.072 * pd) - (0.032 * ad) -
  (0.190 * m2) - (0.065 * p2) - (0.046 * a2) - (0.139 * n3)

eq_index_th[TH & is_11111(eq_raw)] <- 1
eq_new[TH_idx, "eq_5d_3l"] <- round(eq_index_th[TH_idx], 3)

# ----------------------------
# Malaysia  (fixed: removed undefined 'eq_ok')
# ----------------------------
MY_ori <- eq_raw$country == "Malaysia"
MY <- MY_ori & !is.na(eq_condition) & eq_condition
MY_idx <- which(MY)

disut_mo_my <- ifelse(MY & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.084,
                                    ifelse(eq_raw$eq_fo==3, 0.191, NA_real_))),
                      NA_real_)
disut_sc_my <- ifelse(MY & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.097,
                                    ifelse(eq_raw$eq_fo_1==3, 0.160, NA_real_))),
                      NA_real_)
disut_ua_my <- ifelse(MY & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.053,
                                    ifelse(eq_raw$eq_fo_2==3, 0.122, NA_real_))),
                      NA_real_)
disut_pd_my <- ifelse(MY & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.054,
                                    ifelse(eq_raw$eq_fo_3==3, 0.127, NA_real_))),
                      NA_real_)
disut_ad_my <- ifelse(MY & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.081,
                                    ifelse(eq_raw$eq_fo_4==3, 0.086, NA_real_))),
                      NA_real_)

n3_my <- ifelse(
  MY,
  as.numeric(rowSums(cbind(eq_raw$eq_fo==3,
                           eq_raw$eq_fo_1==3,
                           eq_raw$eq_fo_2==3,
                           eq_raw$eq_fo_3==3,
                           eq_raw$eq_fo_4==3), na.rm = TRUE) > 0) * 0.116,
  NA_real_
)

eq_index_my <- 1 - 0.067 - (disut_mo_my + disut_sc_my + disut_ua_my + disut_pd_my + disut_ad_my + n3_my)
eq_index_my[MY & is_11111(eq_raw)] <- 1
eq_new[MY_idx, "eq_5d_3l"] <- round(eq_index_my[MY_idx], 3)

# ----------------------------
# Pakistan (incl. Bangladesh, Nepal, Cambodia, Philippines, Timor-Leste, Vietnam, India)
# ----------------------------
PK_ori <- eq_raw$country %in% c("Pakistan","Bangladesh","Nepal","Cambodia",
                                "Philippines","Timor-Leste","Vietnam","India")
PK <- PK_ori & !is.na(eq_condition) & eq_condition
PK_idx <- which(PK)

disut_mo_pk <- ifelse(PK & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.049,
                                    ifelse(eq_raw$eq_fo==3, 0.279, NA_real_))),
                      NA_real_)
disut_sc_pk <- ifelse(PK & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.057,
                                    ifelse(eq_raw$eq_fo_1==3, 0.217, NA_real_))),
                      NA_real_)
disut_ua_pk <- ifelse(PK & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.040,
                                    ifelse(eq_raw$eq_fo_2==3, 0.280, NA_real_))),
                      NA_real_)
disut_pd_pk <- ifelse(PK & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.035,
                                    ifelse(eq_raw$eq_fo_3==3, 0.214, NA_real_))),
                      NA_real_)
disut_ad_pk <- ifelse(PK & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.036,
                                    ifelse(eq_raw$eq_fo_4==3, 0.181, NA_real_))),
                      NA_real_)

eq_index_pk <- 1 - (disut_mo_pk + disut_sc_pk + disut_ua_pk + disut_pd_pk + disut_ad_pk)
eq_new[PK_idx, "eq_5d_3l"] <- round(eq_index_pk[PK_idx], 3)

# ----------------------------
# Sri Lanka 
# ----------------------------
LK_ori <- eq_raw$country == "Sri Lanka"
LK <- LK_ori & !is.na(eq_condition) & eq_condition
LK_idx <- which(!is.na(LK) & LK)

disut_mo_lk <- ifelse(LK & !is.na(eq_raw$eq_fo),
                      ifelse(eq_raw$eq_fo==1, 0,
                             ifelse(eq_raw$eq_fo==2, 0.166,
                             ifelse(eq_raw$eq_fo==3, 1.071, NA_real_))),
                      NA_real_)
disut_sc_lk <- ifelse(LK & !is.na(eq_raw$eq_fo_1),
                      ifelse(eq_raw$eq_fo_1==1, 0,
                             ifelse(eq_raw$eq_fo_1==2, 0.119,
                             ifelse(eq_raw$eq_fo_1==3, 0.337, NA_real_))),
                      NA_real_)
disut_ua_lk <- ifelse(LK & !is.na(eq_raw$eq_fo_2),
                      ifelse(eq_raw$eq_fo_2==1, 0,
                             ifelse(eq_raw$eq_fo_2==2, 0.071,
                             ifelse(eq_raw$eq_fo_2==3, -0.419, NA_real_))),
                      NA_real_)
disut_pd_lk <- ifelse(LK & !is.na(eq_raw$eq_fo_3),
                      ifelse(eq_raw$eq_fo_3==1, 0,
                             ifelse(eq_raw$eq_fo_3==2, 0.057,
                             ifelse(eq_raw$eq_fo_3==3, 0.300, NA_real_))),
                      NA_real_)
disut_ad_lk <- ifelse(LK & !is.na(eq_raw$eq_fo_4),
                      ifelse(eq_raw$eq_fo_4==1, 0,
                             ifelse(eq_raw$eq_fo_4==2, 0.044,
                             ifelse(eq_raw$eq_fo_4==3, 0.194, NA_real_))),
                      NA_real_)

mo2ua2_lk <- 0.053  * as.numeric(LK & !is.na(eq_raw$eq_fo)   & eq_raw$eq_fo  == 2 &
                                       !is.na(eq_raw$eq_fo_2) & eq_raw$eq_fo_2== 2)
mo3sc3_lk <- (-0.182)* as.numeric(LK & !is.na(eq_raw$eq_fo)   & eq_raw$eq_fo  == 3 &
                                       !is.na(eq_raw$eq_fo_1) & eq_raw$eq_fo_1== 3)
mo3ua3_lk <- (-0.208)* as.numeric(LK & !is.na(eq_raw$eq_fo)   & eq_raw$eq_fo  == 3 &
                                       !is.na(eq_raw$eq_fo_2) & eq_raw$eq_fo_2== 3)
mo3pd3_lk <- (-0.181)* as.numeric(LK & !is.na(eq_raw$eq_fo)   & eq_raw$eq_fo  == 3 &
                                       !is.na(eq_raw$eq_fo_3) & eq_raw$eq_fo_3== 3)
mo3ad3_lk <- (-0.113)* as.numeric(LK & !is.na(eq_raw$eq_fo)   & eq_raw$eq_fo  == 3 &
                                       !is.na(eq_raw$eq_fo_4) & eq_raw$eq_fo_4== 3)
sc3ua2_lk <- 0.048  * as.numeric(LK & !is.na(eq_raw$eq_fo_1) & eq_raw$eq_fo_1== 3 &
                                       !is.na(eq_raw$eq_fo_2) & eq_raw$eq_fo_2== 2)
ua3pd3_lk <- 0.078  * as.numeric(LK & !is.na(eq_raw$eq_fo_2) & eq_raw$eq_fo_2== 3 &
                                       !is.na(eq_raw$eq_fo_3) & eq_raw$eq_fo_3== 3)

disut_total_lk <- disut_mo_lk + disut_sc_lk + disut_ua_lk + disut_pd_lk + disut_ad_lk +
                  mo2ua2_lk + mo3sc3_lk + mo3ua3_lk + mo3pd3_lk + mo3ad3_lk +
                  sc3ua2_lk + ua3pd3_lk

# Initialize vector and fill only LK rows
eq_index_lk <- rep(NA_real_, nrow(eq_raw))

eq_index_lk[LK_idx] <- 1 - 0.152 - disut_total_lk[LK_idx]

eq_index_lk[intersect(LK_idx, which(is_11111(eq_raw)))] <- 1

eq_new[LK_idx, "eq_5d_3l"] <- round(eq_index_lk[LK_idx], 3)

# ---------------
# Set to 0 if died prior to day 28 OR func_status_fo == 2
other_eq_condition <- (eq_raw$sub_died_pri_day28 == 1) | (eq_raw$func_status_fo == 2)
eq_new[other_eq_condition, "eq_5d_3l"] <- 0

# ===========
# FBIS
eq_new[which(eq_condition), "fbis_score"] <- eq_raw[which(eq_condition), "fbis_score"]
eq_new[which(other_eq_condition), "fbis_score"] <- 0

#
eq_new <- as.data.frame(eq_new)

#####
# Discharge
del_data_3 <- c("redcap_event_name", "redcap_repeat_instrument", 
                "redcap_repeat_instance", "f03_infection_hospital_outcome_complete")

del_data_3_index <- which(names(data[[3]]) %in% del_data_3)
# d28
data_4 <- c("recordid", "d28_date", "d28_status", "d28_death_date")
data_4_index <- which(names(data[[4]]) %in% data_4)
# mv,icu,readmission
del_data_7 <- c("redcap_event_name", "redcap_repeat_instrument",
                "redcap_repeat_instance", "f07c_admission_progress_complete")
del_data_7_index <- which(names(data[[7]]) %in% del_data_7)

#####
# Merge all into one dataframe
add_list <- list(df_baseline, 
                 data[[3]][, -del_data_3_index], 
                 data[[4]][, data_4_index], 
                 data[[7]][, -del_data_7_index], 
                 sofa_new, 
                 severity_new, 
                 eq_new, 
                 pitt_new[, c("recordid", "pitt_score", "qpitt_score", "UTI_source")],
                 spec_date_index)

df_baseline_all <- reduce(add_list, left_join, by = "recordid") 

# Trans "" to NA
df_baseline_all[df_baseline_all == ""] <- NA
#
df_baseline_all <- as.data.frame(df_baseline_all)
#####
# Generate new variables 
###
# mortality (final status)
# ho_dischargestatus == [DEAD or MORIBUND (Discharged to die at home)]
# sub_died_pri_day28 == 1
##
# mortality date (form ho_discharge_date or d28_death_date, on day 28 from the last
# infection onset)
###
# first 28 status (within 28 days after index infection onset)
# first28_date (onset_date + 28 days)
# first28_observed_date (compare first28_date and mortality date, chose the earlier)
# first28_death (death_date - onset_date) 
# first28_patient_days (for standardized rate)
###
# length before infection onset
#####
df_mortality <- matrix(NA, nrow = nrow(df_baseline_all), ncol = 4)
colnames(df_mortality) <- c("recordid", "mortality", "mortality_date", "first28_date")

# recordid
df_mortality[, "recordid"] <- df_baseline_all$recordid

# "mortality" and "mortality_date"
system.time({
  condition1 <- df_baseline_all$ho_dischargestatus %in% c("DEAD", "MORIBUND")
  condition2 <- df_baseline_all$sub_died_pri_day28 == 1
  condition3 <- df_baseline_all$ho_dischargestatus %in% c("ALIVE", "LAMA")

  all_na <- is.na(df_baseline_all$ho_dischargestatus) & is.na(df_baseline_all$sub_died_pri_day28)

  df_mortality[, "mortality"] <- ifelse(
    condition1 | condition2,
    1,
    ifelse(all_na, NA, 0)
  )

  mortality_rows <- which(df_mortality[, "mortality"] == 1)

  for (i in mortality_rows) {
    if (!is.na(df_baseline_all$ho_discharge_date[i]) & !is.na(df_baseline_all$d28_death_date[i])) {
      df_mortality[i, "mortality_date"] <- as.character(df_baseline_all$d28_death_date[i])
    } else if (!is.na(df_baseline_all$d28_death_date[i])) {
      df_mortality[i, "mortality_date"] <- as.character(df_baseline_all$d28_death_date[i])
    } else if (!is.na(df_baseline_all$ho_discharge_date[i])) {
      df_mortality[i, "mortality_date"] <- as.character(df_baseline_all$ho_discharge_date[i])
    } else if ((condition3[i] || condition2[i]) & !is.na(df_baseline_all$d28_death_date[i])) {
      df_mortality[i, "mortality_date"] <- as.character(df_baseline_all$d28_death_date[i])
    } else {
      df_mortality[i, "mortality_date"] <- NA
    }
  }
})

# "first28_date"
df_baseline_all$inf_onset <- as.Date(df_baseline_all$inf_onset, format="%Y-%m-%d")
df_mortality[, "first28_date"] <- as.character(df_baseline_all$inf_onset + 28)

# 
df_mortality <- as.data.frame(df_mortality)

df_mortality[, "mortality_date"] <- as.Date(df_mortality[, "mortality_date"], format="%Y-%m-%d")
df_mortality[, "first28_date"] <- as.Date(df_mortality[, "first28_date"])

# "first28_observed_date", "first28_death", "first28_patient_days", "length_before_onset"
df_mortality <- df_mortality %>%
  mutate(
    first28_observed_date = case_when(
      is.na(mortality_date) ~ first28_date,
      TRUE ~ pmin(first28_date, mortality_date)
    ),
    first28_death = case_when(
      first28_observed_date == mortality_date ~ 1,
      !is.na(first28_observed_date) ~ 0,
      TRUE ~ NA_integer_
    ),
    first28_patient_days = as.numeric(first28_observed_date - df_baseline_all$inf_onset),
    length_before_onset = as.numeric(df_baseline_all$inf_onset - as.Date(df_baseline_all$hpd_adm_date))
  )

###
df_baseline_all <- left_join(df_baseline_all, df_mortality, by = "recordid")

###
## length(mv, ICU, readmission) during the follow-up 28 days since index infection onset 
# Function to determine from which group to start calculation
determine_start_group <- function(start_dates, end_dates, inf_onset) {
  inf_onset_date <- as.Date(inf_onset, format="%Y-%m-%d")
  for (i in seq_along(end_dates)) {
    start_date <- as.Date(start_dates[[i]], format="%Y-%m-%d")
    end_date <- as.Date(end_dates[[i]], format="%Y-%m-%d")
    if (!is.na(start_date) && !is.na(end_date) && !is.na(inf_onset_date) &&
        start_date < (inf_onset_date + 28) && end_date > inf_onset_date) {
      return(i)
    }
  }
  return(NA_integer_)
}

# Define a function to calculate durations and convert character to Date
calculate_durations <- function(start_dates, end_dates) {
  durations <- map2_dbl(start_dates, end_dates, ~ {
    if (is.na(.x) | is.na(.y)) {
      return(NA_real_)
    } else {
      return(as.numeric(.y - .x))
    }
  })
  durations
}

# Define a function to calculate total duration with the specific NA handling logic from a specified group
calculate_total_duration <- function(start_dates, end_dates, group_to_use) {
  if (is.na(group_to_use)) {
    return(NA_real_)
  }
  total_duration <- 0
  for (i in group_to_use:length(start_dates)) {
    if (!is.na(start_dates[i]) && !is.na(end_dates[i])) {
      total_duration <- total_duration + as.numeric(end_dates[i] - start_dates[i])
    }
  }
  total_duration
}

#
df_baseline_all <- df_baseline_all %>%
  rowwise() %>%
  mutate(
    start_dates_mv = list(as.Date(unlist(dplyr::c_across(starts_with("mv_ap_") & ends_with("_2"))), format="%Y-%m-%d")),
    end_dates_mv = list(as.Date(unlist(dplyr::c_across(starts_with("mv_ap_") & ends_with("_3"))), format="%Y-%m-%d")),
    group_to_use_mv = determine_start_group(start_dates_mv, end_dates_mv, inf_onset),
    total_mv = calculate_total_duration(start_dates_mv, end_dates_mv, group_to_use_mv),
    
    start_dates_icu = list(as.Date(unlist(dplyr::c_across(starts_with("icu_hd_ap_") & ends_with("_2"))), format="%Y-%m-%d")),
    end_dates_icu = list(as.Date(unlist(dplyr::c_across(starts_with("icu_hd_ap_") & ends_with("_3"))), format="%Y-%m-%d")),
    group_to_use_icu = determine_start_group(start_dates_icu, end_dates_icu, inf_onset),
    total_icu = calculate_total_duration(start_dates_icu, end_dates_icu, group_to_use_icu)
  ) %>%
  mutate(
    across(starts_with("mv_ap_") & ends_with("_2"), ~ as.Date(.x, format="%Y-%m-%d")),
    across(starts_with("mv_ap_") & ends_with("_3"), ~ as.Date(.x, format="%Y-%m-%d")),
    across(starts_with("icu_hd_ap_") & ends_with("_2"), ~ as.Date(.x, format="%Y-%m-%d")),
    across(starts_with("icu_hd_ap_") & ends_with("_3"), ~ as.Date(.x, format="%Y-%m-%d")),
    across(starts_with("readm_ap_") & ends_with("_2"), ~ as.Date(.x, format="%Y-%m-%d")),
    across(starts_with("readm_ap_") & ends_with("_3"), ~ as.Date(.x, format="%Y-%m-%d"))
  ) %>%
  ungroup()

###
first28_progress <- matrix(NA, nrow = nrow(df_baseline_all), ncol = 4)
colnames(first28_progress) <- c("max_mv", "max_icu", "first28_mv", "first28_icu")

# before & after
system.time({
  for (i in 1:nrow(df_baseline_all)) {
    group_to_use_mv <- df_baseline_all$group_to_use_mv[i]
    if (!is.na(group_to_use_mv)) {
      mv_cols <- grep("^mv_ap_.*_2$", names(df_baseline_all))
      start_date_mv <- as.Date(unlist(df_baseline_all[i, mv_cols]))[group_to_use_mv]
      inf_onset_date <- as.Date(df_baseline_all$inf_onset[i])
      if (!is.na(start_date_mv) && !is.na(inf_onset_date)) {
        if (start_date_mv <= inf_onset_date) {
          first28_progress[i, "max_mv"] <- as.numeric(inf_onset_date - start_date_mv) + 28
        } else {
          first28_progress[i, "max_mv"] <- 28 - as.numeric(start_date_mv - inf_onset_date)
        }
      } else {
        first28_progress[i, "max_mv"] <- NA
      }
    }
  }
})

# 
system.time({
  for (i in 1:nrow(df_baseline_all)) {
    group_to_use_mv <- df_baseline_all$group_to_use_mv[i]
    if (!is.na(group_to_use_mv)) {
      mv_cols <- grep("^mv_ap_.*_2$", names(df_baseline_all))
      start_date_mv <- as.Date(unlist(df_baseline_all[i, mv_cols]))[group_to_use_mv]
      inf_onset_date <- as.Date(df_baseline_all$inf_onset[i])
      total_mv <- df_baseline_all$total_mv[i]
      if (!is.na(start_date_mv) && !is.na(inf_onset_date) && !is.na(total_mv)) {
        if ((start_date_mv <= inf_onset_date) & (first28_progress[i, "max_mv"] >= total_mv)) {
          first28_progress[i, "first28_mv"] <- total_mv - as.numeric(inf_onset_date - start_date_mv)
        } else if ((start_date_mv <= inf_onset_date) & (first28_progress[i, "max_mv"] < total_mv)) {
          first28_progress[i, "first28_mv"] <- 28
        } else if ((start_date_mv > inf_onset_date) & (first28_progress[i, "max_mv"] >= total_mv)) {
          first28_progress[i, "first28_mv"] <- total_mv
        } else if ((start_date_mv > inf_onset_date) & (first28_progress[i, "max_mv"] < total_mv)) {
          first28_progress[i, "first28_mv"] <- 28 - as.numeric(start_date_mv - inf_onset_date)
        } else {
          first28_progress[i, "first28_mv"] <- NA
        }
      } else {
        first28_progress[i, "first28_mv"] <- NA
      }
    }
  }
})

# Adding ICU Data
system.time({
  for (i in 1:nrow(df_baseline_all)) {
    group_to_use_icu <- df_baseline_all$group_to_use_icu[i]
    if (!is.na(group_to_use_icu)) {
      icu_cols <- grep("^icu_hd_ap_.*_2$", names(df_baseline_all))
      start_date_icu <- as.Date(unlist(df_baseline_all[i, icu_cols]))[group_to_use_icu]
      inf_onset_date <- as.Date(df_baseline_all$inf_onset[i])
      if (!is.na(start_date_icu) && !is.na(inf_onset_date)) {
        if (start_date_icu <= inf_onset_date) {
          first28_progress[i, "max_icu"] <- as.numeric(inf_onset_date - start_date_icu) + 28
        } else {
          first28_progress[i, "max_icu"] <- 28 - as.numeric(start_date_icu - inf_onset_date)
        }
      } else {
        first28_progress[i, "max_icu"] <- NA
      }
    }
  }
})

system.time({
  for (i in 1:nrow(df_baseline_all)) {
    group_to_use_icu <- df_baseline_all$group_to_use_icu[i]
    if (!is.na(group_to_use_icu)) {
      icu_cols <- grep("^icu_hd_ap_.*_2$", names(df_baseline_all))
      start_date_icu <- as.Date(unlist(df_baseline_all[i, icu_cols]))[group_to_use_icu]
      inf_onset_date <- as.Date(df_baseline_all$inf_onset[i])
      total_icu <- df_baseline_all$total_icu[i]
      if (!is.na(start_date_icu) && !is.na(inf_onset_date) && !is.na(total_icu)) {
        if ((start_date_icu <= inf_onset_date) & (first28_progress[i, "max_icu"] >= total_icu)) {
          first28_progress[i, "first28_icu"] <- total_icu - as.numeric(inf_onset_date - start_date_icu)
        } else if ((start_date_icu <= inf_onset_date) & (first28_progress[i, "max_icu"] < total_icu)) {
          first28_progress[i, "first28_icu"] <- 28
        } else if ((start_date_icu > inf_onset_date) & (first28_progress[i, "max_icu"] >= total_icu)) {
          first28_progress[i, "first28_icu"] <- total_icu
        } else if ((start_date_icu > inf_onset_date) & (first28_progress[i, "max_icu"] < total_icu)) {
          first28_progress[i, "first28_icu"] <- 28 - as.numeric(start_date_icu - inf_onset_date)
        } else {
          first28_progress[i, "first28_icu"] <- NA
        }
      } else {
        first28_progress[i, "first28_icu"] <- NA
      }
    }
  }
})

df_baseline_all <- df_baseline_all %>%
  mutate(
    max_mv = first28_progress[, "max_mv"],
    first28_mv = first28_progress[, "first28_mv"],
    max_icu = first28_progress[, "max_icu"],
    first28_icu = first28_progress[, "first28_icu"]
  )

# For those without ICU, mv
update_column <- function(df, condition_col, target_col) {
  condition <- !is.na(df[[condition_col]]) & is.na(df[[target_col]])
  df[[target_col]][condition] <- 0
  return(df)  
}

#
df_baseline_all <- update_column(df_baseline_all, "icu_hd_ap", "first28_icu")
df_baseline_all <- update_column(df_baseline_all, "mv_ap", "first28_mv")

# Length of hospital stay (the first discharge)
# Earlier date (ho_discharge_date, mortality_date)
df_baseline_all$first_discharge_date <- pmin(df_baseline_all$ho_discharge_date, df_baseline_all$mortality_date, na.rm = TRUE)

df_baseline_all$first_discharge_date <- as.Date(df_baseline_all$first_discharge_date, format="%Y-%m-%d")

df_baseline_all$first_los <- as.numeric(as.Date(df_baseline_all$first_discharge_date) - as.Date(df_baseline_all$hpd_adm_date))


# Delete error data for healthcare-associated BSI
error_rows <- which(df_baseline_all$infection_types == "Healthcare-associated BSI" & 
              (df_baseline_all$cmb_overnight_rhc_surgery != "Y" | is.na(df_baseline_all$cmb_overnight_rhc_surgery)))

df_errors_bsi <- df_baseline_all[error_rows, ]

# Delete error BSI
df_baseline_all <- df_baseline_all[-error_rows, ]

```
# Microbiology
```{r}
#####
# All episodes
# Remove unnecessary variables
del_col_data_2 <- data[[2]] %>% 
  select(starts_with("antibiotic_"))

del_col_data_2_indices <- which(names(data[[2]]) %in% colnames(del_col_data_2))

all_episode <- data[[2]][,-del_col_data_2_indices]
# Add organism infection types
df_baseline_vap <- df_baseline[which(df_baseline$infection_types == "VAP"),]
df_baseline_bsi <- df_baseline[-which(df_baseline$infection_types == "VAP"),]

df_all_episode <- split(all_episode, all_episode$redcap_event_name)

all_episode_vap <- left_join(df_all_episode$vap_episode_arm_1,
                             df_baseline_vap, by = "recordid")
all_episode_bsi <- left_join(df_all_episode$bsi_episode_arm_1,
                             df_baseline_bsi, by = "recordid")
all_vap_bsi <- list(all_episode_vap, all_episode_bsi)
#####
# Select index episode 
episode_index <- all_episode[which(data[[2]]$f2_episode_index == 1),]
df_episode <- split(episode_index, episode_index$redcap_event_name)
#
vap_index <- left_join(df_episode$vap_episode_arm_1, df_baseline_vap, by = "recordid")
bsi_index <- left_join(df_episode$bsi_episode_arm_1, df_baseline_bsi, by = "recordid")

# All index episode
vap_index <- vap_index[!is.na(vap_index$infection_types), ]
bsi_index <- bsi_index[!is.na(bsi_index$infection_types), ]

vap_index <- vap_index[which(vap_index$redcap_repeat_instance == 1), ]
bsi_index <- bsi_index[which(bsi_index$redcap_repeat_instance == 1), ]

# Combine 
vap_bsi_index <- rbind.data.frame(vap_index, bsi_index)
```
# Add age to the AST
```{r}
ast_add_age_inf <- df_baseline_all[, c("recordid", "age_new", "infection_types")]
ast_add_age <- df_baseline_all[, c("recordid", "age_new")]

all_ast_merged <- left_join(all_ast_merged, ast_add_age_inf, by = "recordid")
all_ast_merged_index <- left_join(all_ast_merged_index, ast_add_age, by = "recordid")
```
# Exclude error enrollments
```{r}
# BSI exclusion
bsi_excl_org <- c("Salmonella", "Listeria")
row_exclude_bsi_ast <- which(all_ast_merged$org_names_all %in% bsi_excl_org & all_ast_merged$infection_types %in% c("Hospital-acquired BSI", "Healthcare-associated BSI"))
row_exclude_bsi_ast_index <- which(all_ast_merged_index$org_names_all %in% bsi_excl_org & all_ast_merged_index$infection_types %in% c("Hospital-acquired BSI", "Healthcare-associated BSI"))

all_ast_merged_exclude_bsi <- all_ast_merged[row_exclude_bsi_ast,]
all_ast_merged_index_exclude_bsi <- all_ast_merged_index[row_exclude_bsi_ast_index,]

all_ast_merged <- all_ast_merged[-row_exclude_bsi_ast,]
all_ast_merged_index <- all_ast_merged_index[-row_exclude_bsi_ast_index,]

bsi_exclude_comm_id <- setdiff(all_ast_merged_exclude_bsi$recordid, all_ast_merged$recordid)
row_exclude_bis_baseline <- which(df_baseline_all$recordid %in% bsi_exclude_comm_id)
df_baseline_all_excl_bsi <- df_baseline_all[row_exclude_bis_baseline,]
df_baseline_all <- df_baseline_all[-row_exclude_bis_baseline,]

# VAP exclusion
vap_excl_org <- c("S. pneumoniae", "Haemophilus", "Coagulase-negative staphylococci (CoNS)", "Mycobacterium", "Enterococcus spp.")
row_exclude_vap_ast <- which(all_ast_merged$org_names_all %in% vap_excl_org & all_ast_merged$infection_types == "VAP")
row_exclude_vap_ast_index <- which(all_ast_merged_index$org_names_all %in% vap_excl_org & all_ast_merged_index$infection_types == "VAP")

all_ast_merged_exclude_vap <- all_ast_merged[row_exclude_vap_ast,]
all_ast_merged_index_exclude_vap <- all_ast_merged_index[row_exclude_vap_ast_index,]

all_ast_merged <- all_ast_merged[-row_exclude_vap_ast,]
all_ast_merged_index <- all_ast_merged_index[-row_exclude_vap_ast_index,]

vap_exclude_comm_id <- setdiff(all_ast_merged_exclude_vap$recordid, all_ast_merged$recordid)
row_exclude_vap_baseline <- which(df_baseline_all$recordid %in% vap_exclude_comm_id)
df_baseline_all_excl_vap <- df_baseline_all[row_exclude_vap_baseline,]
df_baseline_all <- df_baseline_all[-row_exclude_vap_baseline,]

```
# Complete CPIS score for VAP in baseline
```{r}
# Culture of TA
# Combine pathogen_group for each recordid (index)
cul_data_index <- all_ast_merged_index %>%
  filter(!is.na(org_names_all)) %>%
  select(recordid, org_names_all, Class) %>%
  distinct(recordid, org_names_all, .keep_all = TRUE) %>%
  group_by(recordid) %>%
  summarize(org_combined = paste(org_names_all, collapse = ", "),
            pathogen_group_combined = paste(Class, collapse = ", "),
            .groups = 'drop') %>%
  as.data.frame()

# Define a function to sort alphabetically and standardize combinations
standardize_combination <- function(combination) {
  elements <- unlist(strsplit(combination, ", "))
  standardized <- paste(sort(elements), collapse = ", ")
  return(standardized)
}

# Apply the function to the pathogen_group_combined column
cul_data_index$pathogen_group_combined <- sapply(cul_data_index$pathogen_group_combined, standardize_combination)

###
## Type of pathogen 
#  Gram-negative only 
#  Gram-positive only
#  Gram-negative with fungal
#  Mixed (GNB + GPB)
#  Polymicrobial  
#  Fungal only
# Define a function to classify the combinations
classify_combination <- function(combination) {
  if (is.na(combination)) {
    return(NA)
  }
  if (combination == "GNB") {
    return("Gram-negative bacteria (GNB)")
  } else if (combination == "GPB") {
    return("Gram-positive bacteria (GPB)")
  } else if (combination == "Fungi") {
    return("Fungi")
  } else if (combination == "Fungi, GNB") {
    return("GNB with fungi")
  } else if (combination == "Fungi, GPB") {
    return("GPB with fungi")
  } else if (combination == "GNB, GPB") {
    return("Mixed (GNB + GPB)")
  } else if (combination == "GPB, GPB" || combination == "GNB, GNB") {
    return("Polymicrobial (2GNB or 2 GPB)")
  } else {
    return("Unknown") 
  }
}

cul_data_index$pathogen_combined_types_ori <- sapply(cul_data_index$pathogen_group_combined, classify_combination)

# Create a new column with recoded factor levels for pathogen_combined_types
cul_data_index$pathogen_combined_types <- recode(cul_data_index$pathogen_combined_types_ori,
  "Fungi" = "Fungi", 
  "Gram-negative bacteria (GNB)" = "Gram-negative bacteria",
  "Gram-positive bacteria (GPB)" = "Gram-positive bacteria",
  .default = "Polymicrobial",
  .missing = NA_character_
)

# 
cul_data_index$pathogen_combined_types <- factor(cul_data_index$pathogen_combined_types,
  levels = c("Gram-negative bacteria", "Gram-positive bacteria", "Fungi", "Polymicrobial")
)

###
all_ast_merged_index <- left_join(all_ast_merged_index, cul_data_index, by = "recordid")
# 
cul_data_new_index <- cul_data_index %>%
  mutate(culture_ta = ifelse(grepl("GPB", pathogen_group_combined, fixed = TRUE), 1, 0))

#
cpis_new <- as.data.frame(cpis_new)
cpis_new[,"culture_ta"] <- cul_data_new_index$culture_ta[match(cpis_new$recordid, cul_data_new_index$recordid)]

# Total cpis score
cpis_items <- c("temperature", "wbc", "tracheal_secretion", 
                "pa_fi", "pulmonary_radiography", "culture_ta")
cpis_items_indices <- which(names(cpis_new) %in% cpis_items)

for (i in cpis_items_indices) {cpis_new[, i] = as.numeric(as.character(cpis_new[, i]))}

#
cpis_new[,"cpis_score"] <- rowSumsWithNA(cpis_new[, cpis_items_indices])

###
# Add CPIS score into the baseline
df_baseline_all[, "cpis_score"] <- cpis_new$cpis_score[match(df_baseline_all$recordid, cpis_new$recordid)]
```
# Antibiotics
```{r}
# Add sepcimen date and infection onset date
anti_date_add <- list(anti_treat_index, spec_date_index, inf_add)
anti_treat_index_new_ori <- reduce(anti_date_add, left_join, by = "recordid")

# Add AST result of WHO list
# Acinetobacter, carbapenem-resistant;
# Enterobacterales, third-generation cephalosporin-resistant
# Enterobacterales, carbapenem-resistant
###
# Organisms
anti_treat_index_new_org <- all_ast_merged_index %>% 
  select("recordid", "org_combined", "pathogen_combined_types") %>%
  distinct()

anti_treat_index_new_ori <- left_join(anti_treat_index_new_ori, 
                                      anti_treat_index_new_org, 
                                      by = "recordid")

# Combine anti_group_pa_ab, anti_group_ent (update anti_group)
pattern_ent <- paste(ent_spec_org, collapse = "|")

anti_treat_index_new_poly <- anti_treat_index_new_ori %>%
  mutate(
    contains_aci = ifelse(str_detect(org_combined, "Acinetobacter spp."), 1, 0),
    contains_ent = ifelse(str_detect(org_combined, pattern_ent), 1, 0),
    contains_pse = ifelse(str_detect(org_combined, "Pseudomonas spp."), 1, 0),
    contains_entc = ifelse(str_detect(org_combined, "Enterococcus spp."), 1, 0),
    contains_sa = ifelse(str_detect(org_combined, "S. aureus"), 1, 0)
  ) 

# Included monomicrobial infection
anti_treat_index_new_mono <- anti_treat_index_new_poly %>%
  filter(
    pathogen_combined_types %in% c("Gram-negative bacteria", "Gram-positive bacteria")
  )

# ------------------------------------------------------------------------------
# Based on AST results, identify the priority pathogens
# Carbapenem-resistant Acinetobacter spp. (CRA & CSA)
id_aci_car_index_r <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "Acinetobacter spp." & all_ast_merged_index$ris_Carbapenem == 1]
id_aci_car_index_s <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "Acinetobacter spp." & all_ast_merged_index$ris_Carbapenem %in% c(2:5)]

# Carbapenem-resistant Pseudomonas spp. (CRP & CSP)
id_pse_car_index_r <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "Pseudomonas spp." & all_ast_merged_index$ris_Carbapenem == 1]
id_pse_car_index_s <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "Pseudomonas spp." & all_ast_merged_index$ris_Carbapenem %in% c(2:5)]

# Vancomycin-resistant Enterococcus spp.
id_entc_van_index_r <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "Enterococcus spp." & all_ast_merged_index$Vancomycin == 1]
id_entc_van_index_s <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "Enterococcus spp." & all_ast_merged_index$Vancomycin %in% c(2:5)]

# Methicillin-resistant Staphylococcus aureus
id_sa_meth_index_r <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "S. aureus" & all_ast_merged_index$Methicillin == 1]
id_sa_meth_index_s <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all == "S. aureus" & all_ast_merged_index$Methicillin %in% c(2:5)]

# Enterobacterales
# CRE
id_ent_car_index_r <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all %in% ent_spec_org & all_ast_merged_index$ris_Carbapenem == 1]

# 3GCRE
id_ent_thir_index_r_ori <- all_ast_merged_index$recordid[all_ast_merged_index$org_names_all %in% ent_spec_org & all_ast_merged_index$`ris_Third-generation cephalosporin` == 1]

id_ent_thir_index_r <- setdiff(id_ent_thir_index_r_ori, id_ent_car_index_r)

# CSE & 3GCSE
id_ent_ast_all <- unique(all_ast_merged_index$recordid[all_ast_merged_index$org_names_all %in% ent_spec_org])

id_ent_thir_index_s <- setdiff(id_ent_ast_all, union(id_ent_car_index_r, id_ent_thir_index_r))

# ----------------------
new_cols_pothogens <- list(
  aci_car = expr(case_when(
    recordid %in% id_aci_car_index_r ~ 1,
    recordid %in% id_aci_car_index_s ~ 0,
    TRUE ~ NA_real_
  )),
  ent_thir = expr(case_when(
    recordid %in% id_ent_thir_index_r ~ 1,
    recordid %in% id_ent_thir_index_s ~ 0,
    TRUE ~ NA_real_
  )),
  ent_car = expr(case_when(
    recordid %in% id_ent_car_index_r ~ 1,
    recordid %in% c(id_ent_thir_index_s, id_ent_thir_index_r) ~ 0,
    TRUE ~ NA_real_
  )),
  pse_car = expr(case_when(
    recordid %in% id_pse_car_index_r ~ 1,
    recordid %in% id_pse_car_index_s ~ 0,
    TRUE ~ NA_real_
  )),
  entc_van = expr(case_when(
    recordid %in% id_entc_van_index_r ~ 1,
    recordid %in% id_entc_van_index_s ~ 0,
    TRUE ~ NA_real_
  )),
  sa_meth = expr(case_when(
    recordid %in% id_sa_meth_index_r ~ 1,
    recordid %in% id_sa_meth_index_s ~ 0,
    TRUE ~ NA_real_
  )),
  ent_car_3gcr = expr(case_when(
    recordid %in% id_ent_car_index_r ~ 2,
    recordid %in% id_ent_thir_index_r ~ 1,
    recordid %in% id_ent_thir_index_s ~ 0,
    TRUE ~ NA_real_
  ))
)

# Update anti_treat_index_new with new columns based on the identified categories
anti_treat_index_new_mono <- anti_treat_index_new_mono %>%
  mutate(!!!new_cols_pothogens)

anti_treat_index_new_poly <- anti_treat_index_new_poly %>%
  mutate(!!!new_cols_pothogens)

# Add drug-pathogen combinations to baseline
df_baseline_all <- df_baseline_all %>%
  mutate(!!!new_cols_pothogens)

#####
# Empirical prescriptions
# Antibiotics were started no more than 24 hours before the onset of infection and 
# were administered for no longer than 48 hours from the time of infection onset.
# Definitive prescriptions
# Antibiotics are given 3-5 days post specimen date.
###
process_antibiotic_treatment_data <- function(data, anti_aw_info) {
  # Empirical prescription period: infection onset -1 to +2 days
  emp_start_range <- data$inf_onset - days(1)
  emp_end_range   <- data$inf_onset + days(2)
  
  # Flag empirical prescriptions
  data$emp <- ifelse(emp_start_range <= data$anti_end & emp_end_range >= data$anti_start, 1, 0)
  
  # Definitive prescription period: specimen date +3 to +5 days
  def_start_range <- data$spec_date + days(3)
  def_end_range   <- data$spec_date + days(5)
  
  # Flag definitive prescriptions
  data$def <- ifelse(def_start_range <= data$anti_end & def_end_range >= data$anti_start, 1, 0)
  
  # Join WHO AWaRe category
  data <- left_join(data, anti_aw_info, by = "anti_names")
  
  return(data)
}

# Add WHO AWaRe category
anti_aw_info <- anti[, c("anti_names", "WHO_AWaRe")]

anti_treat_index_new_mono <- process_antibiotic_treatment_data(anti_treat_index_new_mono, anti_aw_info)
anti_treat_index_new_poly <- process_antibiotic_treatment_data(anti_treat_index_new_poly, anti_aw_info)

```
# Episode for incidence
```{r}
df_epi_inc <- data[[2]] %>% 
  select(recordid, redcap_event_name, redcap_repeat_instance)

episode_for_inc <- left_join(df_epi_inc, df_baseline_all, by = "recordid")

# Find recordid in data[[2]] not in data[[1]] (baseline)
to_remove <- setdiff(data[[2]]$recordid, data[[1]]$recordid)

# Remove those rows from episode_for_inc
episode_for_inc <- episode_for_inc %>% 
  filter(!recordid %in% to_remove)

```
# Error VAP with fungi
```{r}
df_errors_vap <- all_ast_merged_index[which(all_ast_merged_index$pathogen_combined_types == "Fungi" & all_ast_merged_index$infection_types == "VAP"),]
```
# Exclude error BSI and VAP with fungi
```{r}
# List of dataframes to modify
df_list <- list(
  inf_add = inf_add,
  df_baseline_all = df_baseline_all,
  all_vap_bsi = all_vap_bsi,
  vap_bsi_index = vap_bsi_index,
  all_ast_merged = all_ast_merged,
  all_ast_merged_index = all_ast_merged_index,
  anti_treat_index_new = anti_treat_index_new_mono,
  anti_treat_index_new_poly = anti_treat_index_new_poly,
  episode_for_inc = episode_for_inc
)

# Record IDs to exclude
exclude_ids_vap <- df_errors_vap$recordid
exclude_ids_bsi <- df_errors_bsi$recordid

exclude_ids_inf_errors <- union(exclude_ids_vap, exclude_ids_bsi)

length(which(df_baseline_all$recordid %in% exclude_ids_inf_errors))


# Exclude no infection onset date
df_baseline_all[df_baseline_all == ""] <- NA
df_baseline_all_no_inf_date <- df_baseline_all[which(is.na(df_baseline_all$infection_types)),]
no_inf_date_ids <- df_baseline_all_no_inf_date$recordid

exclude_ids <- union(exclude_ids_inf_errors, no_inf_date_ids)

# Apply filtering only to data.frames
df_list <- lapply(df_list, function(df) {
  if (is.data.frame(df)) {
    df %>% filter(!recordid %in% exclude_ids)
  } else {
    df
  }
})

# Restore to individual objects
inf_add <- df_list$inf_add
df_baseline_all <- df_list$df_baseline_all
all_vap_bsi <- df_list$all_vap_bsi
vap_bsi_index <- df_list$vap_bsi_index
all_ast_merged <- df_list$all_ast_merged
all_ast_merged_index <- df_list$all_ast_merged_index
anti_treat_index_new <- df_list$anti_treat_index_new
anti_treat_index_new_poly <- df_list$anti_treat_index_new_poly
episode_for_inc <- df_list$episode_for_inc
```
# Save
```{r}
# Delete testing row
rows_to_delete <- lapply(
  list(inf_add, df_baseline_all, all_vap_bsi, vap_bsi_index,
       all_ast_merged, all_ast_merged_index,
       anti_treat_index_new, anti_treat_index_new_poly, episode_for_inc),
  function(x) {
    rid <- trimws(as.character(x$recordid))
    which(stringr::str_detect(rid, stringr::regex("test", ignore_case = TRUE)))
  }
)

#
data_frames <- list(inf_add, df_baseline_all,
                    all_vap_bsi, vap_bsi_index, 
                    all_ast_merged, all_ast_merged_index,
                    anti_treat_index_new, anti_treat_index_new_poly,
                    episode_for_inc)
#
for (i in seq_along(data_frames)) {
  if (length(rows_to_delete[[i]]) > 0) {
    data_frames[[i]] <- data_frames[[i]][-rows_to_delete[[i]], ]
  }
}

# Save
file_paths <- c(
  "data/clean data/infection_types_index.RData",
  "data/clean data/baseline_outcomes_index.RData",
  "data/clean data/all_vap_bsi.RData",
  "data/clean data/vap_bsi_index.RData",
  "data/clean data/ast_all.RData",
  "data/clean data/ast_all_index.RData",
  "data/clean data/anti_treat_index.RData",
  "data/clean data/anti_treat_index_poly.RData",
  "data/clean data/episode_for_incidence.RData"
)

#
for (i in seq_along(data_frames)) {
  saveRDS(data_frames[[i]], file_paths[i])
} 
```
# Save as excel
```{r}
# Data frames to export
one_sheet_list <- list(
  inf_add,
  df_baseline_all,
  all_ast_merged,
  all_ast_merged_index,
  anti_treat_index_new,
  anti_treat_index_new_poly,
  episode_for_inc,
  all_ast_merged_exclude_bsi,
  all_ast_merged_exclude_vap,
  all_ast_merged_index_exclude_bsi,
  all_ast_merged_index_exclude_vap,
  df_errors_vap,
  df_errors_bsi
)

# File paths
one_sheet_paths <- c(
  "data/clean_data_excel/infection_types_index.xlsx",
  "data/clean_data_excel/baseline_outcomes_index.xlsx",
  "data/clean_data_excel/ast_all.xlsx",
  "data/clean_data_excel/ast_all_index.xlsx",
  "data/clean_data_excel/anti_treat_index.xlsx",
  "data/clean_data_excel/anti_treat_index_poly.xlsx",
  "data/clean_data_excel/episode_for_incidence.xlsx",
  "data/check_data/all_ast_merged_exclude_bsi.xlsx",
  "data/check_data/all_ast_merged_exclude_vap.xlsx",
  "data/check_data/all_ast_merged_index_exclude_bsi.xlsx",
  "data/check_data/all_ast_merged_index_exclude_vap.xlsx",
  "data/check_data/error_vap_fungi.xlsx",
  "data/check_data/error_bsi.xlsx"
)

# Fully coerce all columns to character, even numeric and date
clean_data_frame_to_char <- function(df) {
  df[] <- lapply(df, function(col) {
    if (is.list(col)) {
      sapply(col, function(x) paste(x, collapse = "; "))
    } else {
      as.character(col)
    }
  })
  return(df)
}

# Clean and save
for (i in seq_along(one_sheet_list)) {
  cat("Saving to:", one_sheet_paths[i], "\n")
  df_clean <- clean_data_frame_to_char(one_sheet_list[[i]])
  write.xlsx(df_clean, one_sheet_paths[i], rowNames = FALSE)
}
###
```
# For dashboard
```{r}
# Retain all patients in each dataset
# Save data list
xx_data <- list(
  enrollment = df_baseline_all,
  infection = vap_bsi_index,
  ast_organism_index = all_ast_merged_index,
  org_anti = anti_treat_index_new
)
saveRDS(xx_data, file = "data/clean data/xinxin_data_latest.rds")
```